---
title: "Balance_Tables_TOUPDATE"
author: "Kateri Mouawad"
date: "2025-04-07"
output: html_document
---

#INITIATE SCRIPT

```{r}
# Define a vector of required packages
packages <- c("clusterSEs", "mlogit", "writexl", "dplyr", "readr", "tidyr", 
              "haven", "data.table", "tidyverse", "estimatr", "broom", "kableExtra", 
              "sandwich", "lmtest", "stats", "nnet", "car", "aod", "clubSandwich")

# Install any missing packages
new_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
if (length(new_packages)) install.packages(new_packages, dependencies = TRUE)

# Load the required packages
lapply(packages, library, character.only = TRUE)


```

### Define file paths and load data 

```{r}

# Define the file paths
proj_paths <- list(
  projects = "C:/Users/Kateri/Box/NSF Senegal",
  alternative_projects = "C:/Users/km978/Box/NSF Senegal"
)

# Check if the Kateri path exists and resolve the project path accordingly
if (file.exists(proj_paths$projects)) {
  proj <- kwb.utils::resolve(list(
    projects = proj_paths$projects,
    p1 = "<projects>/Data_Management/Output/Analysis/Balance_Tables"
  ))  
} else {
  proj <- kwb.utils::resolve(list(
    projects = proj_paths$alternative_projects,
    p1 = "<projects>/Data_Management/Output/Analysis/Balance_Tables"
  ))
}


file_path_balance_tables_df <- file.path(proj$p1, "baseline_balance_tables_data_PAP.dta")
balance_df_raw <- read_dta(file_path_balance_tables_df)
balance_df_raw


file_path_asset_index_df <- file.path(proj$p1, "PCA_asset_index_var.dta")
asset_df_raw <- read_dta(file_path_asset_index_df)
asset_df_raw

```



```{r}



# Adding a single categorical variable for household training categories - this is for computing summary stats since I'm keeping the trained_hh variable
# joint_df <- balance_df %>%
#   mutate(
#     group = str_sub(hhid, 3, 4),
#     treatment_group = case_when(
#       group %in% c("0A", "0B") ~ "Control",
#       group %in% c("1A", "1B") ~ "Treatment1",
#       group %in% c("2A", "2B") ~ "Treatment2",
#       group %in% c("3A", "3B") ~ "Treatment3",
#          )
#   ) %>% select(-group)
# 
# names(joint_df)


summary_df <- balance_df_raw %>%
  mutate(
    group = str_sub(hhid, 3, 4),
    treatment_group = case_when(
      group %in% c("0A", "0B") ~ "Control",
      group %in% c("1A", "1B") ~ "Treatment1",
      group %in% c("2A", "2B") ~ "Treatment2",
      group %in% c("3A", "3B") ~ "Treatment3",
      group %in% c("1A", "1B", "2A", "2B", "3A", "3B") & trained_hh == 0 ~ "Local Control"
    )
  ) %>% select(-group)

long_data_sum <- summary_df %>%
  pivot_longer(
    cols = -c(hhid, hhid_village, treatment_group),  # Keep hhid and group as is, pivot all other columns
    names_to = "variable",    # Create a column named "variable" for former column names
    values_to = "value"       # Store values in a column named "value"
  )

  long_data_sum <- long_data_sum %>%
    rename(group = treatment_group)

# Adding a single categorical variable for household training categories - this is for running regressions to avoid multicollinearity with trained_hh
balance_df <- balance_df_raw %>%
  mutate(
    # Extract the two middle characters (e.g., 2A) from hhid
    group = str_sub(hhid, 3, 4),
        # Assign treatment group, ensuring "Local Control" is prioritized
    treatment_group = case_when(
      group %in% c("0A", "0B") ~ "Control",
      group %in% c("1A", "1B") ~ "Treatment1",
      group %in% c("2A", "2B") ~ "Treatment2",
       group %in% c("1A", "1B", "2A", "2B", "3A", "3B") & trained_hh == 0 ~ "Local Control",  # Moved to the top
      group %in% c("3A", "3B") ~ "Treatment3"
    )
  ) %>% select(-group, -trained_hh)
balance_df


```


##Compute summary stats



```{r}


compute_summary_stats <- function(df) {
  df %>%
    mutate(variable = factor(variable, levels = unique(variable))) %>%  # Preserve variable order
    group_by(group, variable) %>%
    summarise(
      mean_value = round(mean(value, na.rm = TRUE), 2),
      sd_value = round(sd(value, na.rm = TRUE), 2),
      N = sum(!is.na(value)),  # Count of non-missing values
      .groups = "drop"
    ) %>%
    pivot_longer(cols = c(mean_value, sd_value, N), names_to = "stat_type", values_to = "stat_value") %>%
    mutate(stat_type = case_when(
      stat_type == "mean_value" ~ "Mean",
      stat_type == "sd_value" ~ "SD",
      stat_type == "N" ~ "N"
    )) %>%
    mutate(stat_type = factor(stat_type, levels = c("Mean", "SD", "N"))) %>%  # Set order of statistics
    arrange(variable, stat_type) %>%
    pivot_wider(names_from = group, values_from = stat_value) %>%
    select(variable, stat_type, everything())  # Ensure variable and stat_type come first
}

summary_table1 <- compute_summary_stats(long_data_sum)

# View output
print(summary_table1)

```

###Clean up summary table
```{R}

summary_table2 <- summary_table1 %>%
  

  
  # Apply two decimal places for numeric columns (Control, Treatment1, etc.)
  mutate(across(where(is.numeric), ~ format(.x, nsmall = 2))) %>%
  
  # Convert everything to character type (for proper formatting)
  mutate(across(everything(), as.character)) %>%
  
  # Add parentheses for SD values (only if stat_type is SD)
  mutate(across(
    Control:Treatment3,  # Apply only to numeric columns
    ~ ifelse(stat_type == "SD", paste0("(", trimws(.), ")"), .)  # Add parentheses for SD values
  )) %>%

  # Select necessary columns: variable, N_values, and treatment columns
  select(variable, everything()) %>%


mutate(
  variable = ifelse(stat_type %in% c("SD", "N"), "", variable),
  stat_type = ifelse(stat_type %in% c("SD", "N"), "", stat_type)
) %>%
  select(-stat_type, -`NA`)


summary_table2

```

###Bring in survey questions and values

```{r}


summary_table3 <- summary_table2 %>%
  mutate(Question = case_when(
    variable == "hhid_village" ~ "Village ID",
    variable == "hhid" ~ "Household ID",
    variable == "trained_hh" ~ "Trained household",
    variable == "hh_age_h" ~ "Household head age",
    variable == "hh_education_level_bin_h" ~ "Indicator for household head with secondary education or higher (1=Yes, 0=No)",
    variable == "hh_education_skills_5_h" ~ "Indicator that household head is literate (1=Yes, 0=No)",
    variable == "hh_gender_h" ~ "Household head gender (1=Male, 0=Female)",
    variable == "hh_numero" ~ "Household size",
    
    variable == "hh_03_" ~ "Indicator for those who worked in domestic agricultural activities in the past 12 months (1=Yes, 0=No) †",
    variable == "hh_10_" ~ "Average weekly hours spent within 1 meter of surface water source, in the past 12 months.",
    variable == "hh_12_6_" ~ "Indicator for those who harvested aquatic vegetation, among those who spent time near a water source in the past 12 months. (1=Yes, 0=No)",
    variable == "hh_16_" ~ "Average weekly hours spent producing, purchasing, or applying fertilizer in the past 12 months (among those near a water source).",
    variable == "hh_15_2" ~ "Indicator for making fertilizer (compost) among those who spent time near a water source (1=Yes, 0=No)",
    
    variable == "hh_26_" ~ "Indicator if currently enrolled in formal school (1=Yes, 0=No, asked about children) †",
    variable == "hh_27_" ~ "Indicator if attended non-formal school or training? (1=Yes, 0=No, asked about children) †",
    variable == "hh_29_01" ~ "Indicator for primary level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_02" ~ "Indicator for secondary middle level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_03" ~ "Indicator for secondary higher level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_04" ~ "Indicator for upper secondary education (1=Yes, 0=No, asked about children)",
    variable == "hh_31_bin" ~ "Indicator if student completed studies or moved to next class for 2022/2023 (1=Yes, 0=No, asked about children)",
    variable == "hh_37_" ~ "Indicator if missed >1 consecutive week of school due to illness in the past 12 months (1=Yes, 0=No, asked about children) †",
    variable == "hh_38_" ~ "Number of attended school days in the past week (asked about children)",
    
    variable == "living_01_bin" ~ "Indicator for selected tap water as main drinking source (1=Yes, 0=No)",
    variable == "game_A_total" ~ "Total paid for Game A (CFA)",
    variable == "game_B_total" ~ "Total paid for Game B (CFA)",
    
    variable == "TLU" ~ "Tropical livestock units",
    variable == "agri_6_15" ~ "Number of cultivated plots",
    variable == "agri_6_32_bin" ~ "Indicator if used any organic fertilizer (1=Yes, 0=No)",
    variable == "agri_6_36_bin" ~ "Indicator if used any inorganic/chemical fertilizer (1=Yes, 0=No)",
    variable == "total_land_ha" ~ "Total land cultivated (hectares)",
    variable == "agri_6_34_comp_any" ~ "Used any compost on any parcel (1=Yes, 0=No) †",
    
    variable == "agri_income_01" ~ "Indicator if engaged in paid agricultural work in last 12 months (1=Yes, 0=No) †",
    variable == "agri_income_05" ~ "Amount received for agricultural work (FCFA), among those who responded yes to working in agriculture",
    
    variable == "beliefs_01_bin" ~ "Probability of contracting bilharzia (1=Strongly agree/Agree) +",
    variable == "beliefs_02_bin" ~ "Probability of household member contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_03_bin" ~ "Probability of a child contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_04_bin" ~ "Agree: Village land should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_05_bin" ~ "Agree: Village water sources should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_06_bin" ~ "Agree: Right to products from own land (1=Yes, 0=No) +",
    variable == "beliefs_07_bin" ~ "Agree: Right to products from community land worked on (1=Yes, 0=No) +",
    variable == "beliefs_08_bin" ~ "Agree: Right to products from community water sources fished in (1=Yes, 0=No) +",
    variable == "beliefs_09_bin" ~ "Agree: Right to products from community water sources harvested from (1=Yes, 0=No) +",
    
    variable == "health_5_3_bin" ~ "Indicator for bilharzia or diarrhea in the past 12 months (1=Yes, 0=No, among those reporting illness)",
    variable == "health_5_6_" ~ "Indicator for Diagnosed with schistosomiasis (1=Yes, 0=No) †",
    
    variable == "num_water_access_points" ~ "Number of village water access points",
    variable == "q_51" ~ "Distance to nearest healthcare center (km) [village level]",
    variable == "target_village" ~ "Indicator if auction village (1=Yes, 0=No)",
    
    TRUE ~ variable  # Default case
  ))

summary_table3

summary_table_complete <- summary_table3 %>% select(Question, everything()) %>%
  rename(Variable = variable,
         `Private Treatment` = Treatment1,
         `Public Treatment` = Treatment2, 
         `Private and Public Treatment` = Treatment3)
summary_table_complete
#%>%   filter(variable != "target_village")
```

####Export summary table to HTML

```{r}

setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Analysis/Balance_Tables")
#Create table with footnotes using kableExtra
summary_table_complete %>%
  kable(format = "html", escape = FALSE, caption = "Baseline Summary Statistics") %>%
  footnote(
general = "Table reports mean values, with standard deviations shown in parentheses below each mean, and the number of observations listed beneath the standard deviations by treatment arm.",
symbol = c(
  "Binary variables were created from Likert scale responses based on their distribution.",
  "'I Don't Know' responses (coded as 2) have been recoded as missing values."),
    symbol_manual = c("+", "†")  # Manually set symbols instead of default numbering
  ) %>%
  save_kable("baseline_summary_statsV7.html")

#my_quarto_project/reports/baseline_summary_statsV5.html

```

####Export summary table to Excel

```{r}
# Excel spreadsheet
setwd("C:/Users/Kateri/Box/NSF Senegal/Data_Management/Output/Analysis/Balance_Tables")
# Manually add footnotes as a single row
footnotes <- data.frame(
  Variable = "Footnotes:",
  Mean = "Table reports mean values, with standard deviations shown in parentheses below each mean, and the number of observations listed beneath the standard deviations by treatment arm.",
  SD = "+ Binary variables were created from Likert scale responses based on their distribution.",
  Other = "† 'I Don't Know' responses (coded as 2) have been recoded as missing values."
)

# Ensure all columns are character type to avoid coercion issues
summary_table_complete <- summary_table_complete %>%
  mutate(across(everything(), as.character))

# Bind footnotes to the summary table
summary_table_with_footnotes <- bind_rows(summary_table_complete, footnotes)

# Save to Excel
write_xlsx(summary_table_with_footnotes, "baseline_summary_statsV7.xlsx")

```




## Create function for regression coefficients




```{r}

run_all_regressions <- function(data, treatment_col, village_col, vars_to_test) {
  results_list <- list()

  for (var in vars_to_test) {
    tryCatch({
      # Subset and drop rows with NA in outcome
      subset <- data %>% select(all_of(var), all_of(treatment_col), all_of(village_col)) %>% drop_na()

      # Define model
      formula <- as.formula(paste(var, "~", treatment_col))
      model <- lm(formula, data = subset)

      # Clustered variance-covariance
      clustered_vcov <- vcovCL(model, cluster = subset[[village_col]])
      clustered_se <- coeftest(model, vcov = clustered_vcov)

      # Wald test for F-statistic and p-value
      wald <- waldtest(model, vcov = clustered_vcov, test = "F")
      f_stat <- round(wald[2, "F"], 2)
      f_pval <- round(wald[2, "Pr(>F)"], 3)

      # Sample size used
      n_obs <- as.character(nobs(model))

      # Extract control group stats (intercept)
      control_mean <- as.character(round(clustered_se[1, 1], 2))
      control_se <- as.character(round(clustered_se[1, 2], 2))

      # Extract treatment comparisons
      coef_names <- rownames(clustered_se)[-1]
      stats <- as.character(round(clustered_se[-1, 1], 2))
      pvals <- as.character(round(clustered_se[-1, 4], 2))

      results <- data.frame(
        variable = var,
        comparison = coef_names,
        stat = stats,
        p = pvals,
        control_mean = control_mean,
        control_se = control_se,
        N = n_obs,
        f_statistic = as.character(f_stat),
        f_p_value = as.character(f_pval),
        row.names = NULL,
        stringsAsFactors = FALSE
      )

      results_list[[var]] <- results
    }, error = function(e) {
      # In case of error, return NA for the variable
      results_list[[var]] <- data.frame(
        variable = var,
        comparison = NA,
        stat = NA,
        p = NA,
        control_mean = NA,
        control_se = NA,
        N = NA,
        f_statistic = NA,
        f_p_value = NA,
        row.names = NULL,
        stringsAsFactors = FALSE
      )
    })
  }

  final_results <- bind_rows(results_list)
  return(final_results)
}


#Run regressions for the baseline variables
 vars_to_test_reg <- setdiff(names(balance_df), c("hhid", "hhid_village", "treatment_group"))
 vars_to_test_reg
    regression_results <- run_all_regressions(balance_df, 'treatment_group', 'hhid_village', vars_to_test_reg)

# Print the combined results
print(regression_results)

```

#### compute FDR adjusted p-values

```{r}
compute_fdr_qvalues <- function(regression_results) {

  # Apply Benjamini-Hochberg correction to regression p-values
  regression_results <- regression_results %>%
      mutate(q_value = as.character(round(p.adjust(p, method = "BH"), 2)))  # Adjust and round q-values # Adjusting only regression p-values

  return(regression_results)  # Return the updated regression table with q-values
}

# Run the function on regression results
regression_results_qvals <- compute_fdr_qvalues(regression_results)

# Print results
print(regression_results_qvals)
```

#### create complete balance table

```{r}

subtable <- regression_results_qvals %>%
  select(variable, control_mean, control_se) #%>%
  # pivot_longer(cols = c(control_mean, control_se), names_to = "stat_type", values_to = "value") %>%
  # mutate(stat_type = ifelse(stat_type == "control_mean", "Mean", "SD"))  # Rename for clarity

subtable <- subtable %>%
  distinct(variable, control_mean, control_se, .keep_all = TRUE)

# Pivot the table to have variables as rows and comparisons as columns
balance_tablev1 <- regression_results_qvals %>%
   select(-control_mean,-control_se) %>%
  rename(q = q_value)    %>%
  pivot_wider(names_from = comparison, values_from = c(stat, p, q))

balance_tablev1
# Rearrange to stack t-stats and p-values in rows

balance_tablev2 <- balance_tablev1 %>%
  pivot_longer(
    cols = -c(variable,  f_statistic, f_p_value, N),
    names_to = 'comparison',
    values_to = 'value'
  ) %>%
  separate(comparison, into = c('type', 'comparison'), sep = '_', extra = 'merge') %>%
  pivot_wider(names_from = comparison, values_from = value)

balance_tablev2


balance_tablev3 <- balance_tablev2 %>%
  left_join(subtable, by = "variable")
balance_tablev3


balance_tablev4 <- balance_tablev3 %>%
  mutate(
    f_statistic = ifelse(
      type == "p",
      paste0("(", sprintf("%.2f", round(as.numeric(f_p_value), 2)), ")"),
      as.character(f_statistic)
    )
  )


balance_tablev4
  
 balance_tablev5 <- balance_tablev4 %>%
  # Ensure f-stat values remain unchanged except for p-values
  mutate(across(starts_with("control_mean"), ~ ifelse(type == "p", as.character(control_se), as.character(.)))) 
  balance_tablev5
 
  
  
balance_tablev6 <- balance_tablev5 %>%
  # Format p-values with parentheses and add significance stars
  mutate(across(c(`treatment_groupLocal Control`, `treatment_groupTreatment1`, `treatment_groupTreatment2`, `treatment_groupTreatment3`), 
    ~ as.character(ifelse(
      grepl("p", type), 
      paste0("(", trimws(.), ifelse(as.numeric(.) <= 0.01, "**", ifelse(as.numeric(.) <= 0.05, "*", "")), ")"), 
      .))))

  
 balance_tablev6 
 
balance_tablev7 <- balance_tablev6 %>%
  # Add brackets around numeric q-values in each cell
 mutate(across(c(`treatment_groupLocal Control`, `treatment_groupTreatment1`, `treatment_groupTreatment2`, `treatment_groupTreatment3`), 
 ~ as.character(ifelse(
    grepl("q", type),
    paste0("[", trimws(.x), ifelse(as.numeric(.x) <= 0.01, "**", ifelse(as.numeric(.x) <= 0.05, "*", "")), "]"),
    .x))))
 

balance_tablev7

```
```{r}
balance_tablev7

balance_tablev8
```


####Add survey questions and values 

```{r}

balance_tablev8 <- balance_tablev7 %>%
  mutate(
    variable = if_else(type == "p" & !is.na(type), "", variable),
    control_mean = ifelse(
      type == "p",
      paste0("(", sprintf("%.2f", round(as.numeric(control_se), 2)), ")"),
      as.character(control_mean)),# Clear variable when type == "(p)" and type is not NA
    #control_mean = if_else(type == "p" & !is.na(type), control_se, control_mean),
    N = if_else(type == "p" & !is.na(type), "", N),
    type = if_else(type == "p" & !is.na(type), "", as.character(type)),  # Clear type when type == "(p)", leave other values unchanged
    f_statistic = if_else(type == "q" & !is.na(type), "", f_statistic),
    variable = if_else(type == "q" & !is.na(type), "", variable), 
    N = if_else(type == "q" & !is.na(type), "", N),
    control_mean = if_else(type == "q" & !is.na(type), "", control_mean),# Clear variable when type == "(p)" and type is not NA
    type = if_else(type == "q" & !is.na(type), "", as.character(type))
 # Clear type when type == "(p)", leave other values unchanged
  
  ) %>%
  select(-f_p_value, -control_se)  # Remove the 'type' column after modification

 balance_tablev8


balance_tablev9 <- balance_tablev8 %>%
  mutate(across(everything(), 
                ~ ifelse(. %in% c("[NaNNA]", "(NaNNA)"), NA, .)))
balance_tablev9
# Print the modified final_table


balance_tablev10 <- balance_tablev9 %>%
mutate(Question = case_when(
    variable == "hhid_village" ~ "Village ID",
    variable == "hhid" ~ "Household ID",
    variable == "trained_hh" ~ "Trained household",
    variable == "hh_age_h" ~ "Household head age",
    variable == "hh_education_level_bin_h" ~ "Indicator for household head with secondary education or higher (1=Yes, 0=No)",
    variable == "hh_education_skills_5_h" ~ "Indicator that household head is literate (1=Yes, 0=No)",
    variable == "hh_gender_h" ~ "Household head gender (1=Male, 0=Female)",
    variable == "hh_numero" ~ "Household size",
    
    variable == "hh_03_" ~ "Indicator for those who worked in domestic agricultural activities in the past 12 months (1=Yes, 0=No) †",
    variable == "hh_10_" ~ "Average weekly hours spent within 1 meter of surface water source, in the past 12 months.",
    variable == "hh_12_6_" ~ "Indicator for those who harvested aquatic vegetation, among those who spent time near a water source in the past 12 months. (1=Yes, 0=No)",
    variable == "hh_16_" ~ "Average weekly hours spent producing, purchasing, or applying fertilizer in the past 12 months (among those near a water source).",
    variable == "hh_15_2" ~ "Indicator for making fertilizer (compost) among those who spent time near a water source (1=Yes, 0=No)",
    
    variable == "hh_26_" ~ "Indicator if currently enrolled in formal school (1=Yes, 0=No, asked about children) †",
    variable == "hh_27_" ~ "Indicator if attended non-formal school or training? (1=Yes, 0=No, asked about children) †",
    variable == "hh_29_01" ~ "Indicator for primary level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_02" ~ "Indicator for secondary middle level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_03" ~ "Indicator for secondary higher level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_04" ~ "Indicator for upper secondary education (1=Yes, 0=No, asked about children)",
    variable == "hh_31_bin" ~ "Indicator if student completed studies or moved to next class for 2022/2023 (1=Yes, 0=No, asked about children)",
    variable == "hh_37_" ~ "Indicator if missed >1 consecutive week of school due to illness in the past 12 months (1=Yes, 0=No, asked about children) †",
    variable == "hh_38_" ~ "Number of attended school days in the past week (asked about children)",
    
    variable == "living_01_bin" ~ "Indicator for selected tap water as main drinking source (1=Yes, 0=No)",
    variable == "game_A_total" ~ "Total paid for Game A (CFA)",
    variable == "game_B_total" ~ "Total paid for Game B (CFA)",
    
    variable == "TLU" ~ "Tropical livestock units",
    variable == "agri_6_15" ~ "Number of cultivated plots",
    variable == "agri_6_32_bin" ~ "Indicator if used any organic fertilizer (1=Yes, 0=No)",
    variable == "agri_6_36_bin" ~ "Indicator if used any inorganic/chemical fertilizer (1=Yes, 0=No)",
    variable == "total_land_ha" ~ "Total land cultivated (hectares)",
    variable == "agri_6_34_comp_any" ~ "Used any compost on any parcel (1=Yes, 0=No) †",
    
    variable == "agri_income_01" ~ "Indicator if engaged in paid agricultural work in last 12 months (1=Yes, 0=No) †",
    variable == "agri_income_05" ~ "Amount received for agricultural work (FCFA), among those who responded yes to working in agriculture",
    
    variable == "beliefs_01_bin" ~ "Probability of contracting bilharzia (1=Strongly agree/Agree) +",
    variable == "beliefs_02_bin" ~ "Probability of household member contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_03_bin" ~ "Probability of a child contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_04_bin" ~ "Agree: Village land should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_05_bin" ~ "Agree: Village water sources should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_06_bin" ~ "Agree: Right to products from own land (1=Yes, 0=No) +",
    variable == "beliefs_07_bin" ~ "Agree: Right to products from community land worked on (1=Yes, 0=No) +",
    variable == "beliefs_08_bin" ~ "Agree: Right to products from community water sources fished in (1=Yes, 0=No) +",
    variable == "beliefs_09_bin" ~ "Agree: Right to products from community water sources harvested from (1=Yes, 0=No) +",
    
    variable == "health_5_3_bin" ~ "Indicator for bilharzia or diarrhea in the past 12 months (1=Yes, 0=No, among those reporting illness)",
    variable == "health_5_6_" ~ "Indicator for Diagnosed with schistosomiasis (1=Yes, 0=No) †",
    
    variable == "num_water_access_points" ~ "Number of village water access points",
    variable == "q_51" ~ "Distance to nearest healthcare center (km) [village level]",
    variable == "target_village" ~ "Indicator if auction village (1=Yes, 0=No)",
    
    TRUE ~ variable  # Default case
  ))

  balance_tablev10  

names(balance_tablev10)

balance_tablev11 <- balance_tablev10 %>%
  rename(
    Variable = variable,
    N = N,  # Keep N as is
    `F-test` = f_statistic,
    Type = type,  # Optional: keep or drop depending on usage
    `Local Control` = `treatment_groupLocal Control`,
    `Private Treatment` = `treatment_groupTreatment1`,
    `Public Treatment` = `treatment_groupTreatment2`,
    `Public & Private Treatment` = `treatment_groupTreatment3`,
    `Control Mean` = control_mean,
    Question = Question
  )
balance_tablev11

# final_table
# 
# 
desired_column_order <- c(
       "N",
       "Control Mean",
       "Local Control",
       "Private Treatment",
       "Public Treatment",
       "Public & Private Treatment",
       "F-test")

# Reorder the columns in final_table
final_table <- balance_tablev11 %>%
  select(Question, Variable, all_of(desired_column_order))  # Ensure 'variable' stays the first column

# # Print the modified final_table
 print(final_table)




```



#OUTPUT TABLE WITH JOINT F TEST


```{r}
setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Analysis/Balance_Tables")

final_table %>%
  kable(format = "html", escape = FALSE, caption = "Baseline Balance Table") %>%
  footnote(
    general = c(
      "LR chi2( 123 ) = ",
      "Prob > chi2 = ",
      "Number of obs = 1,928",
      "Reported statistics are regression coefficients, with p-values in parentheses and false discovery rate (FDR)-adjusted q-values in brackets. Standard errors are clustered at the village level. The means for the Control group are presented in the 'Control Mean' column, with standard errors in parentheses. P-values indicate statistical significance: * denotes significance at the 5% level (p ≤ 0.05), and ** denotes significance at the 1% level (p ≤ 0.01)."
    ),
    symbol = c(
      "Binary variables were derived from Likert scale responses based on their distribution.",
      "Responses marked as 'I Don't Know' (coded as 2) have been recoded as missing values."
    ),
    symbol_manual = c("+", "†")  # Manually set symbols instead of default numbering
  ) %>%
  save_kable("balance_tablev_jointf_6.html")
##balance_tablev11.html = without -9s
```

#####excel output

```{r}

# Excel spreadsheet
setwd("C:/Users/Kateri/Box/NSF Senegal/Data_Management/Output/Analysis/Balance_Tables")

# Define footnotes as a data frame
footnotes <- data.frame(
  Notes = c(
    "LR chi2( 123 ) = ",
    "Prob > chi2 = ",
    "Number of obs = 1,928",
    "Reported statistics are regression coefficients, with p-values in parentheses and false discovery rate (FDR)-adjusted q-values in brackets.",
    "Standard errors are clustered at the village level.",
    "The means for the Control group are presented in the 'Control Mean' column, with standard errors in parentheses.",
    "P-values indicate statistical significance: * denotes significance at the 5% level (p ≤ 0.05), and ** denotes significance at the 1% level (p ≤ 0.01).",
    "+ Binary variables were derived from Likert scale responses based on their distribution.",
    "† Responses marked as 'I Don't Know' (coded as 2) have been recoded as missing values."
  )
)

# Save final table and footnotes in the same Excel file
write_xlsx(list(
  "Baseline Balance Table" = final_table,
  "Footnotes" = footnotes
), "balance_tablev_jointf_6.xlsx")

```






#Asset index summary




```{r}
setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Analysis/Balance_Tables")


# Example summary stats (assuming asset_df_raw is your dataframe)
summary_stats <- asset_df_raw %>%
  summarise(
    asset_index_mean = mean(asset_index, na.rm = TRUE),
    asset_index_sd = sd(asset_index, na.rm = TRUE),
    asset_index_min = min(asset_index, na.rm = TRUE),
    asset_index_max = max(asset_index, na.rm = TRUE),
    
    asset_index_std_mean = mean(asset_index_std, na.rm = TRUE),
    asset_index_std_sd = sd(asset_index_std, na.rm = TRUE),
    asset_index_std_min = min(asset_index_std, na.rm = TRUE),
    asset_index_std_max = max(asset_index_std, na.rm = TRUE)
  )

# Description of how the index was created (included in the note)
index_description <- "
<p style='font-family: Arial, sans-serif;'><strong><u>Note on Asset Index Creation:</u></strong><br><br>
<b>Summary of Variable Creation & Analysis:</b><br>
<b>Variable Creation:</b><br>
<ul>
  <li><strong>Living Condition Variables:</strong> Binary variables were created for the following:</li>
  <ul>
    <li><strong>Water Source (living_01):</strong> Indoor tap, Public tap, or Neighbor's tap (coded as 1).</li>
    <li><strong>Water Treatment (living_02):</strong> Household water treated (1 for Yes).</li>
    <li><strong>Toilet Type (living_04):</strong> Flush toilet with sewer or septic tank (coded as 1).</li>
    <li><strong>Cooking Fuel (living_05):</strong> Gas, Electricity, Petrol/oil/ethanol, Animal waste/dung, or Solar (coded as 1).</li>
    <li><strong>Lighting (living_06):</strong> Electric generator or Solar (coded as 1).</li>
  </ul>
  <li><strong>Asset Index Creation:</strong> A Total Livestock Unit (TLU) variable was created based on the type and number of livestock species (Cattle, Sheep, Goats, etc.).</li>
  <li><strong>Ownership and Agricultural Activities:</strong> Binary variables were created for household ownership of dwelling (agri_6_5_bin) and certain agricultural activities (agri_6_23_bin).</li>
  <li><strong>Data Standardization:</strong> Continuous variables TLU and rooms per member were standardized using z-scores.</li>
  <li><strong>Principal Component Analysis (PCA):</strong> PCA was performed on the binary living conditions variables, the asset-related variables, and standardized continuous variables (TLU and rooms_per_member). The first principal component (PC1) was extracted as the asset index, representing household wealth or socioeconomic status.</li>
  <li><strong>Normalization:</strong> The asset index (asset_index) was standardized (z-score transformation) to create the variable asset_index_std.</li>
</ul>
<b>Final Variables:</b><br>
<ul>
  <li>living_01_bin, living_02_bin, living_05_bin, living_06_bin, agri_6_5_bin, agri_6_23_bin, TLU, rooms_per_member, asset_index, asset_index_std</li>
</ul>
</p>
"

# Combine summary statistics into a table
output_table <- tibble(
  Variable = c("Asset Index", "Asset Index Standardized"),
  Mean = c(summary_stats$asset_index_mean, summary_stats$asset_index_std_mean),
  SD = c(summary_stats$asset_index_sd, summary_stats$asset_index_std_sd),
  Min = c(summary_stats$asset_index_min, summary_stats$asset_index_std_min),
  Max = c(summary_stats$asset_index_max, summary_stats$asset_index_std_max)
)

# Create HTML output with table and note (in standard font)
html_output <- kable(output_table, "html", caption = "Summary Statistics for Asset Index Variables") %>%
  kable_styling() %>%
  add_header_above(c("Variable Summary" = 5)) %>%
  row_spec(0, bold = TRUE)

# Combine the description and the table for the HTML output
html_content <- paste0(
  "<html><head><style>body {font-family: Arial, sans-serif;}</style></head><body>", 
  as.character(html_output), 
  "<br>", 
  index_description,
  "</body></html>"
)

# Specify the file to save the HTML output
output_file <- "asset_index_summary_results_with_notes.html"

# Write the combined content (note + table) to the HTML file
writeLines(html_content, output_file)

# Check output
cat("HTML file has been created: ", output_file)



```











