---
title: "Balance_Tables"
author: "Kateri Mouawad"
date: "2025-01-03"
output: html_document
---

#Read Me

This script processes: 
  * baseline_balance_tables_data_PAP.dta

This script outputs:
  
  
  

#INITIATE SCRIPT

```{r}

#install.packages("writexl")
library(writexl) #to output to excel doc
library(dplyr)
library(readr) #to read in dta's
library(tidyr)
library(haven)
library(data.table)
library(tidyverse)
library(estimatr)
library(broom) 
library(kableExtra) #to output to HTML tables
library(sandwich) #to wrangle data
library(lmtest)  # For likelihood ratio test
library(stats)   #for FDR q-stats
library(nnet)  #to use multilogit regression 


```


### Define file paths and load data 

```{r}

# Define the file paths
proj_paths <- list(
  projects = "C:/Users/Kateri/Box/NSF Senegal",
  alternative_projects = "C:/Users/km978/Box/NSF Senegal"
)

# Check if the Kateri path exists and resolve the project path accordingly
if (file.exists(proj_paths$projects)) {
  proj <- kwb.utils::resolve(list(
    projects = proj_paths$projects,
    p1 = "<projects>/Data_Management/Output/Data_Analysis/Balance_Tables"
  ))  
} else {
  proj <- kwb.utils::resolve(list(
    projects = proj_paths$alternative_projects,
    p1 = "<projects>/Data_Management/Output/Data_Analysis/Balance_Tables"
  ))
}


file_path_balance_tables_df <- file.path(proj$p1, "baseline_balance_tables_data_PAP.dta")
balance_df <- read_dta(file_path_balance_tables_df)
balance_df

```


####Filter data and transform to long


```{r}



# Adding a single categorical variable for household training categories - this is for computing summary stats since I'm keeping the trained_hh variable
joint_df <- balance_df %>%
  mutate(
    group = str_sub(hhid, 3, 4),
    treatment_group = case_when(
      group %in% c("0A", "0B") ~ "Control",
      group %in% c("1A", "1B") ~ "Treatment1",
      group %in% c("2A", "2B") ~ "Treatment2",
      group %in% c("3A", "3B") ~ "Treatment3",
         )
  ) %>% select(-group)


joint_long_data <- joint_df %>%
  pivot_longer(
    cols = -c(hhid, hhid_village, treatment_group),  # Keep hhid and group as is, pivot all other columns
    names_to = "variable",    # Create a column named "variable" for former column names
    values_to = "value"       # Store values in a column named "value"
  )

  joint_long_data <- joint_long_data %>%
    rename(group = treatment_group)
  view(joint_long_data)








summary_df <- balance_df %>%
  mutate(
    group = str_sub(hhid, 3, 4),
    treatment_group = case_when(
      group %in% c("0A", "0B") ~ "Control",
      group %in% c("1A", "1B") ~ "Treatment1",
      group %in% c("2A", "2B") ~ "Treatment2",
      group %in% c("3A", "3B") ~ "Treatment3",
      group %in% c("1A", "1B", "2A", "2B", "3A", "3B") & trained_hh == 0 ~ "Local Control"
    )
  ) %>% select(-group)

long_data_sum <- summary_df %>%
  pivot_longer(
    cols = -c(hhid, hhid_village, treatment_group),  # Keep hhid and group as is, pivot all other columns
    names_to = "variable",    # Create a column named "variable" for former column names
    values_to = "value"       # Store values in a column named "value"
  )

  long_data_sum <- long_data_sum %>%
    rename(group = treatment_group)

# Adding a single categorical variable for household training categories - this is for running regressions to avoid multicollinearity with trained_hh
balance_df <- balance_df %>%
  mutate(
    # Extract the two middle characters (e.g., 2A) from hhid
    group = str_sub(hhid, 3, 4),
        # Assign treatment group, ensuring "Local Control" is prioritized
    treatment_group = case_when(
      group %in% c("0A", "0B") ~ "Control",
      group %in% c("1A", "1B") ~ "Treatment1",
      group %in% c("2A", "2B") ~ "Treatment2",
       group %in% c("1A", "1B", "2A", "2B", "3A", "3B") & trained_hh == 0 ~ "Local Control",  # Moved to the top
      group %in% c("3A", "3B") ~ "Treatment3"
    )
  ) %>% select(-group, -trained_hh)


long_data <- balance_df %>%
  pivot_longer(
    cols = -c(hhid, hhid_village, treatment_group),  # Keep hhid and group as is, pivot all other columns
    names_to = "variable",    # Create a column named "variable" for former column names
    values_to = "value"       # Store values in a column named "value"
  )

  long_data <- long_data %>%
    rename(group = treatment_group)
  view(long_data)

long_data

```


##Compute summary stats



```{r}


compute_summary_stats <- function(df) {
  df %>%
    group_by(group, variable) %>%
    summarise(
      N = sum(!is.na(value)),  # Count of non-missing values
      mean_value = round(mean(value, na.rm = TRUE), 2),
      sd_value = round(sd(value, na.rm = TRUE), 2),
      .groups = "drop"  # Prevents group structure from persisting
    ) %>%
    pivot_longer(cols = c(N, mean_value, sd_value), names_to = "stat_type", values_to = "stat_value") %>%
    mutate(stat_type = case_when(
      stat_type == "mean_value" ~ "Mean",
      stat_type == "sd_value" ~ "SD",
      stat_type == "N" ~ "N"
    )) %>%
    pivot_wider(names_from = group, values_from = stat_value) %>%
    arrange(variable, stat_type) %>%
    select(variable, stat_type, everything()) %>%  # Ensure variable and stat_type come first
    arrange(match(variable, unique(df$variable)))  # Keep original variable order
}



# compute_summary_stats <- function(df) {
#   df %>%
#     group_by(group, variable) %>%
#     summarise(
#       mean_value = round(mean(value, na.rm = TRUE), 2),
#       sd_value = round(sd(value, na.rm = TRUE), 2),
#       .groups = "drop"  # Prevents group structure from persisting
#     ) %>%
#     pivot_longer(cols = c(mean_value, sd_value), names_to = "stat_type", values_to = "stat_value") %>%
#     mutate(stat_type = ifelse(stat_type == "mean_value", "Mean", "SD")) %>%
#     pivot_wider(names_from = group, values_from = stat_value) %>%
#     arrange(variable, stat_type) %>%
#     # This ensures the 'variable' and 'stat_type' columns come first
#     select(variable, stat_type, everything()) %>%
#     # Explicitly ensure 'variable' is ordered as it appears in the original data
#     arrange(match(variable, unique(df$variable))) 
# }

summary_table <- compute_summary_stats(long_data_sum)

# View output
print(summary_table)



```


####Add survey questions and values 

```{r}

# index2 <- which(summary_table$variable == "hh_12_1_")
#   summary_table <- add_row(summary_table, variable = "hh_12", .before = index2)

# Add "hh_13_1_" above "hh_12"
# index3 <- which(summary_table$variable == "hh_13_01")
#   summary_table <- add_row(summary_table, variable = "hh_13", .before = index3)

# index5 <- which(summary_table$variable == "species_1")
#   final_summary_tabletable <- add_row(summary_table, variable = "species", .before = index5)

# summary_table <- summary_table %>%
#   mutate(
#     variable = ifelse(stat_type == "SD" & !is.na(stat_type), "", variable),  # Clear variable for SD rows
#     stat_type = ifelse(stat_type == "SD" & !is.na(stat_type), "", stat_type)  # Clear stat_type for SD rows
#   ) %>%
#   mutate(across(where(is.numeric), ~ format(.x, nsmall = 2))) %>%
#   mutate(across(everything(), as.character)) %>%  # Ensure all columns are character type
#   mutate(across(
#     Control:Treatment3,  # Apply only to numeric columns
#     ~ ifelse(stat_type == "", paste0("(", trimws(.), ")"), .)  # Add parentheses for SD values
#   ))

summary_table <- summary_table %>%
  # Create a separate column for N and store N values in 'N_values'
  mutate(
    N_values = ifelse(stat_type == "N", trimws(as.character(Control)), NA)  # Store N values in 'N_values' column
  ) %>%
  
  # Clear 'variable' and 'stat_type' for SD rows to format properly
  mutate(
    variable = ifelse(stat_type == "SD" & !is.na(stat_type), "", variable),  # Clear variable for SD rows
    stat_type = ifelse(stat_type == "SD" & !is.na(stat_type), "", stat_type)  # Clear stat_type for SD rows
  ) 

summary_table %>%
  
  # Remove rows with stat_type == "N" but preserve the 'N_values' column
  filter(stat_type != "N") %>%
  
  # Apply two decimal places for numeric columns (Control, Treatment1, etc.)
  mutate(across(where(is.numeric), ~ format(.x, nsmall = 2))) %>%
  
  # Convert everything to character type (for proper formatting)
  mutate(across(everything(), as.character)) %>%
  
  # Add parentheses for SD values (only if stat_type is SD)
  mutate(across(
    Control:Treatment3,  # Apply only to numeric columns
    ~ ifelse(stat_type == "", paste0("(", trimws(.), ")"), .)  # Add parentheses for SD values
  )) %>%
  
  # Add 'N_values' column to each of the treatments columns
  mutate(across(Control:Treatment3, ~ ifelse(is.na(N_values), ., N_values), .names = "updated_{.col}")) %>%
  
  # Select necessary columns: variable, N_values, and treatment columns
  select(variable, N_values, everything())



summary_table

summary_table <- summary_table %>%
  mutate(Question = case_when(
    variable == "hhid_village" ~ "Village ID",
    variable == "hhid" ~ "Household ID",
    variable == "trained_hh" ~ "Trained household",
    variable == "hh_age_h" ~ "Household head age",
    variable == "hh_education_level_bin_h" ~ "Indicator for household head with secondary education or higher (1=Yes, 0=No)",
    variable == "hh_education_skills_5_h" ~ "Indicator that household head is literate (1=Yes, 0=No)",
    variable == "hh_gender_h" ~ "Household head gender (1=Male, 0=Female)",
    variable == "hh_numero" ~ "Household size",
    
    variable == "hh_03_" ~ "Indicator for those who worked in domestic agricultural activities (1=Yes, 0=No) †",
    variable == "hh_10_" ~ "Hours per week spent within 1 meter of surface water source",
    variable == "hh_12_6_" ~ "Indicator for those who harvested aquatic vegetation, among those who spent time near a water source (1=Yes, 0=No)",
    variable == "hh_16_" ~ "Hours spent producing, purchasing, or applying fertilizer",
    variable == "hh_15_2" ~ "Indicator for making fertilizer (compost) among those who spent time near a water source (1=Yes, 0=No)",
    
    variable == "hh_26_" ~ "Indicator if currently enrolled in formal school (1=Yes, 0=No, asked about children) †",
    variable == "hh_27_" ~ "Indicator if attended non-formal school or training? (1=Yes, 0=No, asked about children) †",
    variable == "hh_29_01" ~ "Indicator for primary level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_02" ~ "Indicator for secondary middle level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_03" ~ "Indicator for secondary higher level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_04" ~ "Indicator for upper secondary education (1=Yes, 0=No, asked about children)",
    variable == "hh_31_bin" ~ "Indicator if student completed studies or moved to next class (1=Yes, 0=No, asked about children)",
    variable == "hh_37_" ~ "Indicator if missed >1 consecutive week of school due to illness? (1=Yes, 0=No, asked about children) †",
    variable == "hh_38_" ~ "Number of attended school days in the past week (asked about children)",
    
    variable == "living_01_bin" ~ "Indicator for selected tap water as main drinking source (1=Yes, 0=No)",
    variable == "game_A_total" ~ "Total paid for Game A (CFA)",
    variable == "game_B_total" ~ "Total paid for Game B (CFA)",
    
    variable == "TLU" ~ "Tropical livestock units",
    variable == "agri_6_15" ~ "Number of cultivated plots",
    variable == "agri_6_32_bin" ~ "Indicator if used any organic fertilizer (1=Yes, 0=No)",
    variable == "agri_6_36_bin" ~ "Indicator if used any inorganic/chemical fertilizer (1=Yes, 0=No)",
    variable == "total_land_ha" ~ "Total land cultivated (hectares)",
    variable == "agri_6_34_comp_any" ~ "Used any compost on any parcel (1=Yes, 0=No) †",
    
    variable == "agri_income_01" ~ "Indicator if engaged in paid agricultural work in last 12 months (1=Yes, 0=No) †",
    variable == "agri_income_05" ~ "Amount received for agricultural work (FCFA)",
    
    variable == "beliefs_01_bin" ~ "Probability of contracting bilharzia (1=Strongly agree/Agree) +",
    variable == "beliefs_02_bin" ~ "Probability of household member contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_03_bin" ~ "Probability of a child contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_04_bin" ~ "Agree: Village land should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_05_bin" ~ "Agree: Village water sources should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_06_bin" ~ "Agree: Right to products from own land (1=Yes, 0=No) +",
    variable == "beliefs_07_bin" ~ "Agree: Right to products from community land worked on (1=Yes, 0=No) +",
    variable == "beliefs_08_bin" ~ "Agree: Right to products from community water sources fished in (1=Yes, 0=No) +",
    variable == "beliefs_09_bin" ~ "Agree: Right to products from community water sources harvested from (1=Yes, 0=No) +",
    
    variable == "health_5_3_bin" ~ "Indicator for bilharzia or diarrhea in the past 12 months (1=Yes, 0=No, among those reporting illness)",
    variable == "health_5_6_" ~ "Indicator for Diagnosed with schistosomiasis (1=Yes, 0=No) †",
    
    variable == "num_water_access_points" ~ "Number of village water access points",
    variable == "q_51" ~ "Distance to nearest healthcare center (km) [village level]",
    variable == "target_village" ~ "Indicator if auction village (1=Yes, 0=No)",
    
    TRUE ~ variable  # Default case
  ))


summary_table <- summary_table %>% select(Question, everything()) %>%
  select(-"stat_type")  %>%
  rename(Variable = variable,
         `Private Treatment` = Treatment1,
         `Public Treatment` = Treatment2, 
         `Private and Public Treatment` = Treatment3)
summary_table
#%>%   filter(variable != "target_village")


```
###Output table
#####Sum stats - HTML output

```{r}

setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")
#Create table with footnotes using kableExtra
summary_table %>%
  kable(format = "html", escape = FALSE, caption = "Baseline Summary Statistics") %>%
  footnote(
general = "Table presents mean values, with standard deviations in parentheses.",
symbol = c(
  "Binary variables were created from Likert scale responses based on their distribution.",
  "'I Don't Know' responses (coded as 2) have been recoded as missing values."),
    symbol_manual = c("+", "†")  # Manually set symbols instead of default numbering
  ) %>%
  save_kable("_baseline_summary_statsV2.html")


# setwd("C:/Users/km978/Downloads/SenegalGIT/NSF-Senegal/Latex_Output/Balance_Table")
# 
# summary_table %>%
#   kable(format = "latex", booktabs = TRUE, escape = FALSE, caption = "Baseline Summary Statistics") %>%
#   footnote(
#     general = "Table presents mean values, with standard deviations in parentheses.",
#     symbol = c(
#       "Binary variables were created from Likert scale responses based on their distribution.",
#       "'I Don't Know' responses (coded as 2) have been recoded as missing values."
#     ),
#     symbol_manual = c("+", "†")  # Custom symbols instead of default numbering
#   ) %>%
#   save_kable("SS_balance_tableV3.tex")

#Create table with footnotes for excel spreadsheet

```
#####Sum stats - Excel output

```{r}
# Excel spreadsheet
setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")
# Manually add footnotes as a single row
footnotes <- data.frame(
  Variable = "Footnotes:",
  Mean = "Table presents mean values, with standard deviations in parentheses.",
  SD = "+ Binary variables were created from Likert scale responses based on their distribution.",
  Other = "† 'I Don't Know' responses (coded as 2) have been recoded as missing values."
)

# Ensure all columns are character type to avoid coercion issues
summary_table <- summary_table %>%
  mutate(across(everything(), as.character))

# Bind footnotes to the summary table
summary_table_with_footnotes <- bind_rows(summary_table, footnotes)

# Save to Excel
write_xlsx(summary_table_with_footnotes, "_baseline_summary_statsV2.xlsx")

```


##Compute regression coefficients and cluster SEs at the village level



```{r}

#<><<><><>><><<><><>>
#CREATE REGRESSION FUNCTION


# Loops through all variables in vars_to_test.
# Compares each treatment group to the control group (first loop).
# Compares treatment groups to each other (second loop).
# Runs regressions for each comparison.
# Clusters standard errors at the village level.
# Stores and returns regression results in a data frame
 


run_regressions <- function(data, treatment_col, village_col, vars_to_test) {
  results <- list()
  for (var in vars_to_test) {
    treatments <- unique(data[[treatment_col]])
    treatments <- setdiff(treatments, 'Control')
    for (arm in treatments) {
      subset <- data %>% filter(.data[[treatment_col]] %in% c('Control', arm) & variable == var)
      subset$treat <- ifelse(subset[[treatment_col]] == arm, 1, 0)
      model <- lm(value ~ treat, data = subset)
      clustered_se <- coeftest(model, vcov = vcovCL(model, cluster = subset[[village_col]]))
      results <- append(results, list(data.frame(variable = var, comparison = paste('Control vs', arm),
                                                 stat = round(clustered_se[2, 1], 2),
                                                 p = round(clustered_se[2, 4], 2))))
    }
    for (i in 1:(length(treatments) - 1)) {
      for (j in (i + 1):length(treatments)) {
        subset <- data %>% filter(.data[[treatment_col]] %in% c(treatments[i], treatments[j]) & variable == var)
        subset$treat <- ifelse(subset[[treatment_col]] == treatments[j], 1, 0)
        model <- lm(value ~ treat, data = subset)
        clustered_se <- coeftest(model, vcov = vcovCL(model, cluster = subset[[village_col]]))
        results <- append(results, list(data.frame(variable = var, comparison = paste(treatments[i], 'vs', treatments[j]),
                                                 stat = round(clustered_se[2, 1], 2),
                                                 p = round(clustered_se[2, 4], 2))))
                }
              }
            }
            bind_rows(results)
          }




names(balance_df)
    vars_to_test_reg <- setdiff(names(balance_df), c("hhid", "hhid_village", "treatment_group"))
    regression_results <- run_regressions(long_data, 'group', 'hhid_village', vars_to_test_reg)
      #regression_results_test <- run_regressions(long_data, 'group', 'hhid_village', vars_to_test_reg)
      
      
regression_results



#<><<><><>><><<><><>>
#CREATE F-STAT FUNCTION FOR EACH VAR
#<><<><><>><><<><><>>

# Function to perform F-test for each variable
run_f_tests <- function(data, treatment_col, vars_to_test) {
  results <- list()
  
  for (var in vars_to_test) {
    # Construct formula dynamically (e.g., hh_15_2 ~ group)
    formula <- as.formula(paste(var, "~", treatment_col))
        # Run ANOVA for each variable
    anova_result <- aov(formula, data = data)
        # Get the F-statistic and p-value
    f_stat <- summary(anova_result)[[1]]$`F value`[1]
    p_value <- summary(anova_result)[[1]]$`Pr(>F)`[1]
    
    # Store results
    results <- append(results, list(data.frame(variable = var, 
                                               f_statistic = round(f_stat, 2), 
                                               p_value = round(p_value, 2))))
  }
  # Combine and return the results as a data frame
  return(bind_rows(results))
}
    vars_to_test_fstat <- setdiff(names(balance_df), c("hhid", "hhid_village", "treatment_group"))

    f_test_results <- run_f_tests(balance_df, treatment_col = "treatment_group", vars_to_test = vars_to_test_fstat)
    print(f_test_results)




compute_fdr_qvalues <- function(regression_results) {
  
  # Apply Benjamini-Hochberg correction to regression p-values
  regression_results <- regression_results %>%
      mutate(q_value = round(p.adjust(p, method = "BH"), 2))  # Adjust and round q-values # Adjusting only regression p-values
  
  return(regression_results)  # Return the updated regression table with q-values
}

# Run the function on regression results
regression_results_qvals <- compute_fdr_qvalues(regression_results)

# Print results
print(regression_results_qvals)
    
    
    
    
    
    
    
    
    
    
    
    
    
    

#<><<><><>><><<><><>>
#CREATE F-STAT FUNCTION FOR TREATMENT ARM
#<><<><><>><><<><><>>

# # Function to compute Joint F-statistics for each treatment arm (Wide Format)
# run_pairwise_f_test <- function(data, treatment_col, vars_to_test) {
#   results <- list()
#   
#   # Get all treatment arms (excluding 'Control')
#   treatments <- unique(data[[treatment_col]])
#   treatments <- treatments[treatments != "Control"]
#   
#   # Loop over all pairwise combinations of treatments
#   for (i in 1:(length(treatments) - 1)) {
#     for (j in (i + 1):length(treatments)) {
#       # Subset the data for the current pair of treatments
#       subset <- data[data[[treatment_col]] %in% c(treatments[i], treatments[j]), ]
#       
#       # Create regression formula (e.g., hh_15_2 + hh_26_ + hh_27_ ~ group)
#       formula <- as.formula(paste(paste(vars_to_test, collapse = " + "), "~", treatment_col))
#       
#       # Run the regression model
#       model <- lm(formula, data = subset)
#       
#       # Compute F-statistic for the joint test
#       f_stat <- summary(model)$fstatistic[1]
#       p_value <- pf(f_stat, df1 = summary(model)$fstatistic[2], df2 = summary(model)$fstatistic[3], lower.tail = FALSE)
#       
#       # Store results for this pairwise comparison
#       results <- append(results, list(data.frame(treatment_comparison = paste(treatments[i], "vs", treatments[j]),
#                                                  f_statistic = round(f_stat, 2), 
#                                                  p_value = round(p_value, 4))))
#     }
#   }
#   
#   # Combine and return the results as a data frame
#   return(bind_rows(results))
# }
# 
#  vars_to_test_fjoint <- setdiff(names(balance_df), c("hhid", "hhid_village", "treatment_group"))
#     joint_f_test_results <- run_pairwise_f_test(balance_df, treatment_col = "treatment_group", vars_to_test = vars_to_test_fjoint)
# 

   

# Print results
#print(joint_f_test_results)
print(f_test_results)
regression_results



```


##Compute joint f-test

```{r}
setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")
#library(nnet)

model <- multinom(group ~ value, data = joint_long_data)

summary(model)

#View(joint_long_data)
# Create the coefficient names for linearHypothesis
#coefs <- c("valueTreatment1.", "valueTreatment2.", "valueTreatment3.")

# Set up the vector of treatment levels
treatments <- c("Treatment1.", "Treatment2.", "Treatment3.")

# Set up the vector of variables (just "value" here)
variables <- c("value")

# Create the coefficient names using outer to combine treatment levels and variables
coefs <- as.vector(outer(treatments, variables, paste0))

# Print the resulting coefficient names
print(coefs)


# Install and load car package for linearHypothesis
library(car)

# Run the Wald test to check the joint significance of 'value' across the treatments
joint_test <- linearHypothesis(model, coefs)

# Print the results of the joint test
print(joint_test)

#join_f_vars <- setdiff(names(balance_df), c("hhid", "hhid_village", "treatment_group"))


summary(model)
# For Treatment1



joint_test_df <- data.frame(joint_test)
joint_test_df
# Create a kable table with kableExtra
joint_test_html <- joint_test_df %>%
  kable(format = "html", escape = FALSE, caption = "Joint Hypothesis Test Results") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

# Save the output to an HTML file
file_name <- "joint_test_output.html"
save_kable(joint_test_html, file = file_name)

# Inform the user where the file has been saved
cat("The joint test results have been saved to the balance tables file in the output folder.", file_name)



# Remove rows with NA values in predictors to ensure both models use the same dataset
long_data_filtered <- long_data %>%
  filter(!is.na(value) & !is.na(variable))

long_data_filtered

# Convert group to factor and ensure "Control" is the reference category
long_data_filtered$group <- factor(long_data_filtered$group, levels = c("Control", "Local Control", "Treatment1", "Treatment2", "Treatment3"))

# Fit the full model (including predictors)
full_model <- multinom(group ~ value + variable, data = long_data_filtered)
full_model
# Fit the null model (only intercept)
null_model <- multinom(group ~ 1, data = long_data_filtered)
null_model
# Perform the likelihood ratio test (LRT)
lrt_result <- lrtest(full_model, null_model)

# Print LRT result
print(lrt_result)


# # # Prepare data: create outcome variables (1 for treatment arm, 0 otherwise)
# long_data$y_treatment1 <- ifelse(long_data$group == "Treatment1", 1, 0)
# long_data$y_treatment2 <- ifelse(long_data$group == "Treatment2", 1, 0)
# long_data$y_treatment3 <- ifelse(long_data$group == "Treatment3", 1, 0)
# long_data$y_lc_control <- ifelse(long_data$group == "Local Control", 1, 0)
# long_data$y_control <- ifelse(long_data$group == "Control", 1, 0)
# view(long_data)
# # Run multinomial logistic regression (with control as baseline)
# model_f_test <- multinom(cbind(y_treatment1, y_treatment2, y_treatment3, y_lc_control, y_control) ~ value + variable, data = long_data)
# 
# # View model_f_test summary
# summary(model_f_test)
# model_summary <- summary(model_f_test)
# # Perform likelihood ratio tests for the joint null hypothesis
# lr_test <- lrtest(model_f_test)
# lr_test
# summary(lr_test)
# model_summary
# # Extract coefficients and p-values
# #model_summary <- summary(model_f_test)$coefficients
# model_p_values <- model_summary$coefficients[, 4]  # p-values are typically in the 4th column of the coefficients matrix
# 
# q_values <- p.adjust(model_p_values, method = "fdr")
# 
# # Combine results into a tidy table
# f_test_results <- tibble(
#   variable = rownames(model_summary$coefficients),
#   coef_treatment1 = model_summary$coefficients[, 1],  # Coefficients for Treatment1
#   coef_treatment2 = model_summary$coefficients[, 2],  # Coefficients for Treatment2
#   coef_treatment3 = model_summary$coefficients[, 3],  # Coefficients for Treatment3
#   coef_control = model_summary$coefficients[, 4],     # Coefficients for Control
#   p_values = model_p_values,
#   q_values = q_values
# )  %>%
#   select(-q_values)
# 
# 
lrt_result_df <- data.frame(lrt_result)
lrt_result_df

setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")
# Create a kable table with kableExtra
f_test_results_html <- lrt_result_df %>%
  mutate(across(where(is.numeric), as.character)) %>%  # Ensure numbers remain as they are
  kable(format = "html", escape = FALSE, caption = "Likelihood Ratio Test Results") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))


# Save the output to an HTML file
file_name <- "LRT_results_df.html"
save_kable(f_test_results_html, file = file_name)

# Inform the user where the file has been saved
cat("The joint test results have been saved to the balance tables file in the output folder.", file_name)


```


##Create completed table


```{r}


# Pivot the table to have variables as rows and comparisons as columns
final_table <- regression_results_qvals %>%
  rename(q = q_value)    %>%
  pivot_wider(names_from = comparison, values_from = c(stat, p, q))
# Rearrange to stack t-stats and p-values in rows
final_table <- final_table %>%
  pivot_longer(cols = -variable, names_to = 'comparison', values_to = 'value') %>%
  separate(comparison, into = c('type', 'comparison'), sep = '_', extra = 'merge') %>%
  pivot_wider(names_from = comparison, values_from = value)
final_table
# Merge F-statistics data into final_table
final_table <- final_table %>%
  left_join(f_test_results, by = "variable")
final_table

# final_table <- final_table %>%
#   # Ensure f-stat values remain unchanged except for p-values
#   mutate(across(starts_with("f_stat"), ~ ifelse(type == "p", as.character(p_value), as.character(.)))) %>%
#   
#   # Format p-values with parentheses and add significance stars
#   mutate(across(everything(), ~ ifelse(
#     grepl("p", type), 
#     paste0("(", trimws(.x), ifelse(as.numeric(.x) <= 0.01, "**", ifelse(as.numeric(.x) <= 0.05, "*", "")), ")"), 
#     .x))) %>%
#   
#   # Add brackets around q-values
#   mutate(across(everything(), ~ ifelse(
#     grepl("q", stat),  # If the stat column indicates q-values
#     paste0("[", trimws(.x), "]"),  
#     .x))) %>%
#   
#   # Replace character "NaNNA" values with "(NA)" for all columns except variable and type
#   mutate(across(-c(variable, type), ~ ifelse(. == "(NaNNA)", "(NA)", .)))  


final_table <- final_table %>%
  # Ensure f-stat values remain unchanged except for p-values
  mutate(across(starts_with("f_stat"), ~ ifelse(type == "p", as.character(p_value), as.character(.)))) 
  final_table
  
  
final_table <- final_table %>%
  # Format p-values with parentheses and add significance stars
  mutate(across(everything(), ~ as.character(ifelse(
    grepl("p", type), 
    paste0("(", trimws(.x), ifelse(as.numeric(.x) <= 0.01, "**", ifelse(as.numeric(.x) <= 0.05, "*", "")), ")"), 
    .x)))) 

 final_table 
 
final_table <- final_table %>%
  # Add brackets around numeric q-values in each cell
  mutate(across(everything(), ~ as.character(ifelse(
    grepl("q", type), 
    paste0("[", trimws(.x), ifelse(as.numeric(.x) <= 0.01, "**", ifelse(as.numeric(.x) <= 0.05, "*", "")), "]"), 
    .x)))) 



```




```{R}
# Replace the value underneath f_stat with p_value
# final_table <- final_table %>%
#   mutate(across(starts_with("f_stat"), ~ ifelse(type == "p", as.character(p_value), as.character(.)))) %>%
#   mutate(across(everything(), ~ ifelse(grepl("p", type), paste0("(", trimws(.x), ")"), .x)))  # Format p-values with parentheses

# final_table <- final_table %>%
#   mutate(across(starts_with("f_stat"), ~ ifelse(type == "p", as.character(p_value), as.character(.)))) %>%
#   mutate(across(everything(), ~ ifelse(grepl("p", type),
#                                       paste0("(", trimws(.x),
#                                              ifelse(as.numeric(.x) <= 0.01, "**",
#                                                     ifelse(as.numeric(.x) <= 0.05, "*", "")), ")"),
#                                       .x))) %>%
#  
#  mutate(across(everything(), ~ as.character(ifelse(
#     grepl("q", stat),  # If the stat column indicates q-values
#     paste0("[", trimws(.x), "]"),  
#     .x)))) %>%
#   
#    mutate(
#     # Replace character "NaN" values with "NA" for all columns except variable and type
#     across(-c(variable, type), ~ ifelse(. == "(NaNNA)", "(NA)", .))  # Check for character "NaN"
#   )


# joint_f_test_results <- joint_f_test_results %>%
#   pivot_wider(names_from = treatment_comparison, values_from = c(f_statistic, p_value)) %>%
#   rename_with(~ gsub(" ", "_", .), everything())  # Clean up column names
# joint_f_test_results


# Generate f_stats_row from joint_f_test_results
# f_stats_row <- data.frame(
#   variable = "F statistics of Joint F-test:"
# ) %>%
#   bind_cols(joint_f_test_results %>%
#               select(starts_with("f_statistic")) %>%
#               rename_with(~ gsub("f_statistic_", "", .)) %>%    # Remove the 'f_statistic_' prefix
#               rename_with(~ gsub("_", " ", .))) %>%             # Remove the underscores
#   mutate(across(everything(), as.character))  # Convert all to character
# 
# # Print f_stats_row to check
# print(f_stats_row)
# 
# # Generate p_values_row from joint_f_test_results
# p_values_row <- data.frame(
#   variable = "P-value of Joint F-test:"
# ) %>%
#   bind_cols(joint_f_test_results %>%
#               select(starts_with("p_value")) %>%
#               rename_with(~ gsub("p_value_", "", .)) %>%  # Remove the 'p_value_' prefix
#               rename_with(~ gsub("_", " ", .)) %>%       # Remove the underscores
#               mutate(across(everything(), ~ paste0("(", ., ")")))) %>%  # Format p-values with parentheses
#   mutate(across(everything(), as.character))  # Convert all to character
# 
# # Print p_values_row to check
# print(p_values_row)
# 
# 
# final_table <- final_table %>%
#   bind_rows(f_stats_row, p_values_row %>% mutate(
#     `Control vs Treatment3` = NA,  # Add missing column with NA
#     type = NA,                     # Add missing 'type' column with NA
#     `Control vs Treatment1` = NA,  # Add missing 'Control vs Treatment1' column with NA
#     `Control vs Treatment2` = NA,  # Add missing 'Control vs Treatment2' column with NA
#     `Control vs Local Control` = NA,  # Add missing 'Control vs Local Control' column with NA
#     f_statistic = NA,
#     p_value = NA
#   ))

# Print the updated final_table
print(final_table)

```



####Add survey questions and values 

```{r}

final_table <- final_table %>%
  mutate(
    variable = if_else(type == "(pNA)" & !is.na(type), "", variable),  # Clear variable when type == "(p)" and type is not NA
    type = if_else(type == "(pNA)" & !is.na(type), "", as.character(type)),  # Clear type when type == "(p)", leave other values unchanged
    f_statistic = if_else(type == "[qNA]" & !is.na(type), "", f_statistic),
    variable = if_else(type == "[qNA]" & !is.na(type), "", variable),  # Clear variable when type == "(p)" and type is not NA
    type = if_else(type == "[qNA]" & !is.na(type), "", as.character(type))  # Clear type when type == "(p)", leave other values unchanged
  ) %>%
  select(-p_value)  # Remove the 'type' column after modification
final_table


final_table <- final_table %>%
  mutate(across(everything(), 
                ~ ifelse(. %in% c("[NaNNA]", "(NaNNA)"), NA, .)))

# Print the modified final_table
final_table

final_table <- final_table %>%
  mutate(Question = case_when(
    variable == "hhid_village" ~ "Village ID",
    variable == "hhid" ~ "Household ID",
    variable == "trained_hh" ~ "Trained household",
    variable == "hh_age_h" ~ "Household head age",
    variable == "hh_education_level_bin_h" ~ "Indicator for household head with secondary education or higher (1=Yes, 0=No)",
    variable == "hh_education_skills_5_h" ~ "Indicator that household head is literate (1=Yes, 0=No)",
    variable == "hh_gender_h" ~ "Household head gender (1=Male, 0=Female)",
    variable == "hh_numero" ~ "Household size",
    
    variable == "hh_03_" ~ "Indicator for those who worked in domestic agricultural activities (1=Yes, 0=No) †",
    variable == "hh_10_" ~ "Hours per week spent within 1 meter of surface water source",
    variable == "hh_12_6_" ~ "Indicator for those who harvested aquatic vegetation, among those who spent time near a water source (1=Yes, 0=No)",
    variable == "hh_16_" ~ "Hours spent producing, purchasing, or applying fertilizer",
    variable == "hh_15_2" ~ "Indicator for making fertilizer (compost) among those who spent time near a water source (1=Yes, 0=No)",
    
    variable == "hh_26_" ~ "Indicator if currently enrolled in formal school (1=Yes, 0=No, asked about children) †",
    variable == "hh_27_" ~ "Indicator if attended non-formal school or training? (1=Yes, 0=No, asked about children) †",
    variable == "hh_29_01" ~ "Indicator for primary level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_02" ~ "Indicator for secondary middle level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_03" ~ "Indicator for secondary higher level education (1=Yes, 0=No, asked about children)",
    variable == "hh_29_04" ~ "Indicator for upper secondary education (1=Yes, 0=No, asked about children)",
    variable == "hh_31_bin" ~ "Indicator if student completed studies or moved to next class (1=Yes, 0=No, asked about children)",
    variable == "hh_37_" ~ "Indicator if missed >1 consecutive week of school due to illness? (1=Yes, 0=No, asked about children) †",
    variable == "hh_38_" ~ "Number of attended school days in the past week (asked about children)",
    
    variable == "living_01_bin" ~ "Indicator for selected tap water as main drinking source (1=Yes, 0=No)",
    variable == "game_A_total" ~ "Total paid for Game A (CFA)",
    variable == "game_B_total" ~ "Total paid for Game B (CFA)",
    
    variable == "TLU" ~ "Tropical livestock units",
    variable == "agri_6_15" ~ "Number of cultivated plots",
    variable == "agri_6_32_bin" ~ "Indicator if used any organic fertilizer (1=Yes, 0=No)",
    variable == "agri_6_36_bin" ~ "Indicator if used any inorganic/chemical fertilizer (1=Yes, 0=No)",
    variable == "total_land_ha" ~ "Total land cultivated (hectares)",
    variable == "agri_6_34_comp_any" ~ "Used any compost on any parcel (1=Yes, 0=No) †",
    
    variable == "agri_income_01" ~ "Indicator if engaged in paid agricultural work in last 12 months (1=Yes, 0=No) †",
    variable == "agri_income_05" ~ "Amount received for agricultural work (FCFA)",
    
    variable == "beliefs_01_bin" ~ "Probability of contracting bilharzia (1=Strongly agree/Agree) +",
    variable == "beliefs_02_bin" ~ "Probability of household member contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_03_bin" ~ "Probability of a child contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_04_bin" ~ "Agree: Village land should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_05_bin" ~ "Agree: Village water sources should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_06_bin" ~ "Agree: Right to products from own land (1=Yes, 0=No) +",
    variable == "beliefs_07_bin" ~ "Agree: Right to products from community land worked on (1=Yes, 0=No) +",
    variable == "beliefs_08_bin" ~ "Agree: Right to products from community water sources fished in (1=Yes, 0=No) +",
    variable == "beliefs_09_bin" ~ "Agree: Right to products from community water sources harvested from (1=Yes, 0=No) +",
    
    variable == "health_5_3_bin" ~ "Indicator for bilharzia or diarrhea in the past 12 months (1=Yes, 0=No, among those reporting illness)",
    variable == "health_5_6_" ~ "Indicator for Diagnosed with schistosomiasis (1=Yes, 0=No) †",
    
    variable == "num_water_access_points" ~ "Number of village water access points",
    variable == "q_51" ~ "Distance to nearest healthcare center (km) [village level]",
    variable == "target_village" ~ "Indicator if auction village (1=Yes, 0=No)",
    
    TRUE ~ variable  # Default case
  ))

    

final_table

final_table <- final_table %>% 
  select(Question, everything()) %>%
  rename(Variable = variable,
         `Control vs Private Treatment` = `Control vs Treatment1`,
          `Control vs Public Treatment` = `Control vs Treatment2`,
          `Control vs Public & Private Treatment` = `Control vs Treatment3`,
          `Private Treatment vs Public Treatment` = `Treatment1 vs Treatment2`,
          `Private Treatment vs Public & Private Treatment` = `Treatment1 vs Treatment3`,
          `Public Treatment vs Public & Private Treatment` = `Treatment2 vs Treatment3`,
          `Local Control vs Public & Private Treatment` = `Treatment3 vs Local Control`,
          `Local Control vs Private Treatment` = `Treatment2 vs Local Control`,
          `Local Control vs Public Treatment` = `Treatment1 vs Local Control`,
          `F-test` = f_statistic)



        # Define the desired column order
        desired_column_order <- c(
          "Control vs Private Treatment",
          "Control vs Public Treatment",
          "Control vs Local Control",
          "Control vs Public & Private Treatment",
          "Local Control vs Public Treatment",
          "Local Control vs Private Treatment",
          "Local Control vs Public & Private Treatment",
          "Private Treatment vs Public Treatment",
          "Private Treatment vs Public & Private Treatment",
          "Public Treatment vs Public & Private Treatment",
          "F-test"
        )

# Reorder the columns in final_table
final_table <- final_table %>%
  select(Question, Variable, all_of(desired_column_order))  # Ensure 'variable' stays the first column

# Print the modified final_table
print(final_table)

final_table


```

###Output tables

#####Make two tables, one with local control/without

##########Main table - HTML output

```{r}


setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")

final_table %>%
  kable(format = "html", escape = FALSE, caption = "Baseline Balance Table") %>%
  footnote(
 general = "Reported statistics are regression coefficients, with p-values in parentheses and false discovery rate (FDR)-adjusted q-values in brackets. Standard errors are clustered at the village level. P-values indicate statistical significance: * denotes significance at the 5% level (p ≤ 0.05), and ** denotes significance at the 1% level (p ≤ 0.01).",
    symbol = c(
      "Binary variables were derived from Likert scale responses based on their distribution.",
      "Responses marked as 'I Don't Know' (coded as 2) have been recoded as missing values."),
    symbol_manual = c("+", "†")  # Manually set symbols instead of default numbering
  ) %>%
  save_kable("balance_tablev8.html")

# setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")
# knitr::kable(final_table, format = "html") %>% save_kable("balance_tablev3.html")

```


##########Main table - Excel output

```{r}
# Excel spreadsheet
setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")
# Manually add footnotes as a single row
footnotes <- data.frame(
  Variable = "Footnotes:",
  General = "Reported statistics are regression coefficients, with p-values in parentheses and false discovery rate (FDR)-adjusted q-values in brackets. Standard errors are clustered at the village level. P-values indicate statistical significance: * denotes significance at the 5% level (p ≤ 0.05), and ** denotes significance at the 1% level (p ≤ 0.01).",
  Bin_var = "+ Binary variables were created from Likert scale responses based on their distribution.",
  Other = "† 'I Don't Know' responses (coded as 2) have been recoded as missing values."
)

# Ensure all columns are character type to avoid coercion issues
final_table <- final_table %>%
  mutate(across(everything(), as.character))

# Bind footnotes to the summary table
final_table_with_footnotes <- bind_rows(final_table, footnotes)

# Save to final_table_with_footnotes
write_xlsx(final_table_with_footnotes, "balance_tablev2.xlsx")

```


##########Subset table - HTML output

```{r}

setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")


final_table_subset <- final_table  %>%
  select(-starts_with("Local Control"), -`Control vs Local Control`
         )

final_table_subset %>%
  kable(format = "html", escape = FALSE, caption = "Baseline Balance Table") %>%
  footnote(
 general = "Reported statistics are regression coefficients, with p-values in parentheses and false discovery rate (FDR)-adjusted q-values in brackets. Standard errors are clustered at the village level. P-values indicate statistical significance: * denotes significance at the 5% level (p ≤ 0.05), and ** denotes significance at the 1% level (p ≤ 0.01).",
    symbol = c(
      "Binary variables were derived from Likert scale responses based on their distribution.",
      "Responses marked as 'I Don't Know' (coded as 2) have been recoded as missing values."),
    symbol_manual = c("+", "†")  # Manually set symbols instead of default numbering
  ) %>%
  save_kable("_balance_table_subset.html")


#write_xlsx(final_table_subset, "balance_table_subset.xlsx")


```

##########Subset table - Excel output

```{r}
# Excel spreadsheet
setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")
# Manually add footnotes as a single row

# Ensure all columns are character type to avoid coercion issues
final_table_subset <- final_table_subset %>%
  mutate(across(everything(), as.character))

# Bind footnotes to the summary table
table_subset_with_footnotes <- bind_rows(final_table_subset, footnotes)

# Save to final_table_with_footnotes
write_xlsx(table_subset_with_footnotes, "balance_table_Subset.xlsx")
```


```{r}









```






