---
title: "NSF-Senegal Project: Parasitological Analysis Updates"
format:
  html:
    self-contained: true
    html-table-processing: none
    toc: false
    code-fold: false
    theme: default
execute:
  echo: true
---





```{r, echo=FALSE, message=FALSE, warning=FALSE}
# BEGIN HERE - load packages

packages <- c("clusterSEs", "mlogit", "writexl", "dplyr", "readr", "tidyr",
              "haven", "data.table", "tidyverse", "estimatr", "broom", "kableExtra", "haven",
              "sandwich", "lmtest", "stats", "nnet", "car", "aod", "clubSandwich")

# Install any missing packages
new_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
if (length(new_packages)) install.packages(new_packages, dependencies = TRUE)

# Load the required packages without printing any output
invisible(lapply(packages, library, character.only = TRUE))


```




```{r, echo=FALSE, message=FALSE, warning=FALSE}

# BEGIN HERE - load packages
proj_paths <- list(
  projects = "C:/Users/Kateri/Box/NSF Senegal",
  alternative_projects = "C:/Users/km978/Box/NSF Senegal"
)

# Choose the correct project root based on availability
proj_root <- if (file.exists(proj_paths$projects)) {
  proj_paths$projects
} else {
  proj_paths$alternative_projects
}

# Define project subpaths manually using file.path for cross-platform safety
proj <- list(
  p1 = file.path(proj_root, "Data_Management", "Output", "Analysis", "Human_Parasitology", "Analysis_Data")
)

# Full path to Stata file
file_path_infection_df <- file.path(proj$p1, "03_mid_base_analysis_df.dta")

# Load required library
library(haven)

# Read the dataset
infection_df <- read_dta(file_path_infection_df)

```




## Results {.panel-tabset}


::: {.panel-tabset}



### Variable Descriptions

## Notes:
Here are the finalized variables we agreed on in the Google doc. However, if I'm missing anything or should add/remove something, please do let me know.

<table style="width:100%; font-size: 14px;">
  <tr><th>Variable</th><th>Description</th></tr>
  <tr><td>village_id</td><td>Village ID</td></tr>
  <tr><td>village_name</td><td>Village name</td></tr>
  <tr><td>hh_age_</td><td>Individual's age</td></tr>
  <tr><td>hh_gender_</td><td>Individual's gender</td></tr>
  <tr><td>hh_age_resp</td><td>Household respondent's age</td></tr>
  <tr><td>hh_gender_resp</td><td>Household respondent's gender</td></tr>
  <tr><td>hh_10_</td><td>Hours per week spent within 1 meter of surface water source</td></tr>
  <tr><td>hh_26_</td><td>Currently enrolled in formal school? (1=Yes, 2=No)</td></tr>
  <tr><td>hh_32_</td><td>Attends school during the 2023/2024 academic year</td></tr>
  <tr><td>hh_37_</td><td>Missed >1 consecutive week of school due to illness in the past 12 months? (1=Yes, 0=No)</td></tr>
  <tr><td>health_5_2_</td><td>Fell ill in the last 12 months (skip 5.4 if no)</td></tr>
  <tr><td>health_5_3_1_</td><td>Suffered from Malaria</td></tr>
  <tr><td>health_5_3_2_</td><td>Suffered from Bilharzia</td></tr>
  <tr><td>health_5_3_3_</td><td>Suffered from Diarrhea</td></tr>
  <tr><td>health_5_3_6_</td><td>Suffered from Skin issues</td></tr>
  <tr><td>health_5_3_9_</td><td>Suffered from Stomach ache</td></tr>
  <tr><td>health_5_5</td><td>Received medication for schistosomiasis treatment in last 12 months</td></tr>
  <tr><td>health_5_8</td><td>Had blood in urine in the last 12 months</td></tr>
  <tr><td>health_5_9</td><td>Had blood in stool in the last 12 months</td></tr>
  <tr><td>living_01_bin</td><td>Indicator for selected tap water as main source of drinking water</td></tr>
  <tr><td>beliefs_01_bin</td><td>Probability of contracting bilharzia in the next 12 months (1=Strongly agree/Agree)</td></tr>
  <tr><td>beliefs_02_bin</td><td>Probability of household member contracting bilharzia in the next 12 months (1=Strongly agree/Agree)</td></tr>
  <tr><td>beliefs_03_bin</td><td>Probability of a child contracting bilharzia in the next 12 months (1=Strongly agree/Agree)</td></tr>
  <tr><td>hh_12_6_</td><td>Harvest aquatic vegetation</td></tr>
  <tr><td>schisto_indicator</td><td>Indicator for presence of schistosomiasis infection</td></tr>
  <tr><td>sh_inf</td><td>Indicator for Schistosoma haematobium infection</td></tr>
  <tr><td>sm_inf</td><td>Indicator for Schistosoma mansoni infection</td></tr>
  <tr><td>sh_egg_count</td><td>Egg count for Schistosoma haematobium</td></tr>
  <tr><td>sm_egg_count</td><td>Egg count for Schistosoma mansoni</td></tr>
  <tr><td>total_egg</td><td>Total schistosome egg count</td></tr>
  <tr><td>q_23</td><td>Access to running drinking water for drinking (1 = Yes, 0 = No)</td></tr>
  <tr><td>q_24</td><td>Presence of tap water system if running water is available (1 = Yes, 0 = No)</td></tr>
</table>



### Summary Stats

```{r, echo=FALSE, message=FALSE, warning=FALSE}

summary_stats <- function(data, exclude = NULL) {
  # Remove excluded columns
  if (!is.null(exclude)) {
    data <- data[ , !(names(data) %in% exclude)]
  }

  # Keep only numeric columns
  data_numeric <- data[ , sapply(data, is.numeric)]

  # Remove columns where all values are NA
  data_numeric <- data_numeric[ , colSums(!is.na(data_numeric)) > 0, drop = FALSE]

  # Extract variable labels (if present)
  labels <- sapply(data_numeric, function(x) attr(x, "label"))

 # Compute summary statistics
  summary_df <- data.frame(
    Question = labels,
    Variable = names(data_numeric),
    N = sapply(data_numeric, function(x) sum(!is.na(x))),
    Min = round(sapply(data_numeric, function(x) min(x, na.rm = TRUE)), 2),
    Mean = round(sapply(data_numeric, function(x) mean(x, na.rm = TRUE)), 2),
    Max = round(sapply(data_numeric, function(x) max(x, na.rm = TRUE)), 2),
    SD = round(sapply(data_numeric, function(x) sd(x, na.rm = TRUE)), 2),
    row.names = NULL,
    stringsAsFactors = FALSE
  )

  return(summary_df)
}


 paras_sum_stats <- summary_stats(infection_df, exclude = c("hhid_village", "village_name", "hhid", "individ", "identificant","match_score", "round" ))


paras_sum_stats %>%
  mutate(across(where(is.numeric), round, 2)) %>%
  kable(format = "html", table.attr = 'style="width:100%; font-size:14px;"')


```


:::

