#INITIATE HERE - load packages

```{r, echo=FALSE, message=FALSE, warning=FALSE}

# packages <- c("clusterSEs", "mlogit", "writexl", "dplyr", "readr", "tidyr",
#               "haven", "data.table", "tidyverse", "estimatr", "broom", "kableExtra", "haven", "caret",
#               "sandwich", "lmtest", "stats", "nnet", "car", "aod", "clubSandwich", "glmnet", "multiwayvcov")

packages <- c("dplyr", "readr", "tidyr", "stargazer",
             "tidyverse", "kableExtra", "haven", "detectseparation",
              "sandwich", "lmtest", "stats", "clubSandwich", "glmnet", "multiwayvcov")

# install.packages("haven")
# library("haven")
# Install any missing packages
new_packages <- packages[!(packages %in% installed.packages()[, "Package"])]
if (length(new_packages)) install.packages(new_packages, dependencies = TRUE)

# Load the required packages without printing any output
invisible(lapply(packages, library, character.only = TRUE))


```


##Define project specific paths 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
proj_paths <- list(
  projects = "C:/Users/Kateri/Box/NSF Senegal",
  alternative_projects = "C:/Users/km978/Box/NSF Senegal"
)

# Choose the correct project root based on availability
proj_root <- if (file.exists(proj_paths$projects)) {
  proj_paths$projects
} else {
  proj_paths$alternative_projects
}

# Define project subpaths manually using file.path for cross-platform safety
proj <- list(
  p1 = file.path(proj_root, "Data_Management", "Output", "Analysis", "Human_Parasitology", "Analysis_Data")
)

# Full path to Stata file
file_path_infection_df <- file.path(proj$p1, "03_mid_base_analysis_df.dta")

# Read the dataset
infection_df <- read_dta(file_path_infection_df)


```

### Subset data

###### Analysis data

```{r, echo=FALSE, message=FALSE, warning=FALSE}

analysis_df <- infection_df %>%
  select(-Humanwatercontact, -p2_avg, -q_51) %>%
  na.omit()

# nrow(analysis_df)
# nrow(infection_df)


```


##### Training testing data

Here we create Training and Testing data to perform prediction by subsetting 70% of the data as training observations, and 30% as testing. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Total number of observations
n <- nrow(analysis_df)

# Create a vector of shuffled row indices
shuffled_indices <- sample(n)

# Compute the number of training observations (70%)
train_size <- floor(0.7 * n)

# Indices for training and testing
train_indices <- shuffled_indices[1:train_size]
test_indices <- shuffled_indices[(train_size + 1):n]

# Subset the dataframes
train_df <- analysis_df[train_indices, ]
test_df <- analysis_df[test_indices, ]

# Check the sizes
cat("Training set size:", nrow(train_df), "\n")
cat("Testing set size:", nrow(test_df), "\n")

```



# Summary Stats
•	Compute Summary Statistics: We will calculate descriptive statistics for the selected variables 
**Variables:**

- **N** (sample size)

- **Min**

- **Mean**

- **Max**

- **Standard Deviation (SD)**

```{r, echo=FALSE, message=FALSE, warning=FALSE}
      


summary_stats <- function(data, exclude = NULL) {
  # Remove excluded columns
  if (!is.null(exclude)) {
    data <- data[ , !(names(data) %in% exclude)]
  }

  # Keep only numeric columns
  data_numeric <- data[ , sapply(data, is.numeric)]

  # Remove columns where all values are NA
  data_numeric <- data_numeric[ , colSums(!is.na(data_numeric)) > 0, drop = FALSE]

  # Extract variable labels (if present)
  labels <- sapply(data_numeric, function(x) attr(x, "label"))

 # Compute summary statistics
  summary_df <- data.frame(
    Question = labels,
    Variable = names(data_numeric),
    N = sapply(data_numeric, function(x) sum(!is.na(x))),
    Min = round(sapply(data_numeric, function(x) min(x, na.rm = TRUE)), 2),
    Mean = round(sapply(data_numeric, function(x) mean(x, na.rm = TRUE)), 2),
    Max = round(sapply(data_numeric, function(x) max(x, na.rm = TRUE)), 2),
    SD = round(sapply(data_numeric, function(x) sd(x, na.rm = TRUE)), 2),
    row.names = NULL,
    stringsAsFactors = FALSE
  )

  return(summary_df)
}

##on full set of data
 paras_sum_stats <- summary_stats(infection_df, exclude = c("hhid_village", "village_name", "hhid", "individ", "identificant","match_score", "round" ))
```
 
Here are the summary stats for the complete set of pre-selected variables, which includes rows with any missings.  
 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
 
 kable(paras_sum_stats, format = "html", caption = "Summary Statistics for Infection Data") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE, position = "left") %>%
  scroll_box(width = "100%")

        # saveRDS(paras_sum_stats, file = "C:/Users/Kateri/Box/NSF Senegal/Data_Management/Output/Analysis/Human_Parasitology/Tables/paras_sum_stats")
```  

##### Analysis Data Summary Stats

Here are the summary stats for the actual data I use to run the analysis, which drops rows with any missings, and I removed variables with high amounts of missings (Humanwatercontact, p2_avg) and q_51 since we'll be using q_51_W99 (winsorized at the 99th percentile)

```{r, echo=FALSE, message=FALSE, warning=FALSE}          
 paras_sum_stats_ad <- summary_stats(analysis_df, exclude = c("hhid_village", "village_name", "hhid", "individ", "identificant","match_score", "round" ))

 
 kable(paras_sum_stats_ad, format = "html", caption = "Summary Statistics for Analysis Data") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE, position = "left") %>%
  scroll_box(width = "100%")
 
   # saveRDS(paras_sum_stats_ad, file = "C:/Users/Kateri/Box/NSF Senegal/Data_Management/Output/Analysis/Human_Parasitology/Tables/paras_sum_stats_ad")

```

# BEGIN ANALYSIS

This Analysis portion is broken down into 3 parts for each of our outcome variables of interest: 

• sh_inf (S. haematobium Infection indicator), constructed using the parasitological data by:

  - **Equals 1 if egg count from either urine filtration (fu_p1 or fu_p2) is greater than 0; otherwise 0.     Indicates S. haematobium infection (urinary schistosomiasis).**

• sm_inf (S. mansoni infection indicator), constructed using the parasitological data by:

  - **Equals 1 if egg count from any of the four stool slides (p1_kato1_k1_pg, p1_kato2_k2_peg, p2_kato1_k1_epg,      p2_kato2_k2_epg) is greater than 0; otherwise 0. Indicates S. mansoni infection (intestinal     schistosomiasis).**


• sm_sh_inf S. mansoni AND S. haematobium infection indicator),

  - **constructed if sm_inf OR sh_inf = 1.**

# SH_INF

•	Run Lasso regression to determine which variables show the highest predictive power to help determine covariates. 


### Lasso Regression

```{r, echo=FALSE, message=FALSE, warning=FALSE}


exclude_vars <- c("hhid_village", "village_name", "hhid", "individ", 
                  "identificant", "match_score", "round", "sh_inf")  # Exclude outcome too

# Grab all other column names
sh_covariates <- setdiff(names(analysis_df), exclude_vars)

  # Create predictor matrix
  sh_x <- data.matrix(analysis_df[, sh_covariates])
  sh_y <- analysis_df$sh_inf

#perform k-fold cross-validation to find optimal lambda value
sh1 <- cv.glmnet(sh_x, sh_y, family = "binomial", alpha = 1)

sh1_best_lambda <- sh1$lambda.min

#produce plot of test MSE by lambda value
plot(sh1) 


#find coefficients of best model
sh1_best_model <- glmnet(sh_x, sh_y, alpha = 1, lambda = sh1_best_lambda)
coef(sh1_best_model)


# Extract coefficients at best lambda
sh_mat <- coef(sh1_best_model, s = sh1_best_lambda)

# Convert to named vector and find non-zero coefficients
sh_vars_raw <- rownames(sh_mat)[sh_mat[, 1] != 0]

# Remove intercept from selected vars
sh_vars <- setdiff(sh_vars_raw, c("(Intercept)")) #confirm the precise variables we're interested in


#print(sh_vars)

kable(sh_vars, format = "html", caption = "Best Predictors for sh_inf") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE, position = "left") %>%
  scroll_box(width = "100%")

```

### Logit Model

A logistic regression model will be specified using the selected individual-level and community-level covariates.

**Covariates:**

- **Individual-level**: age, gender, self-reported health status (e.g., blood in stool/urine).
- **Community-level**: village predictors (e.g., mass of submerged vegetation, snail prevalence, community survey data).


```{r}

sh_vars_final <- setdiff(names(analysis_df), exclude_vars)

sh_y <- "sh_inf"
# Build formula string
sh_formula <- paste(sh_y, "~", paste(sh_vars, collapse = " + "))

# Fit logistic regression model
sh_model <- glm(as.formula(sh_formula), data = train_df, family = "binomial")

#sh_cse <- vcovCL(sh_model, cluster = train_df$hhid_village)

# Apply coeftest with clustered SE
#sh_model_cse <- coeftest(sh_model, vcov. = sh_cse) KRM - commenting out as we don't need this for classification models

print(sh_model)

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# Install if you don't have it
# library(detectseparation)
# 
# # Run detection on your logistic model formula and data
# # Create model matrix and response
# glm(as.formula(sh_formula), data = train_df, family = binomial("logit"), method ="detect_separation")
# 
# # Assume you have a data.frame called train_df and a vector of variable names: sh_vars
# # And your outcome variable is called 'sh_inf'
# 
# problematic_vars <- c()
# 
# for (var in sh_vars) {
#   # Build the formula for a single predictor
#   f <- as.formula(paste("sh_inf ~", var))
#   
#   # Try to fit the model
#   fit <- tryCatch(
#     glm(f, data = train_df, family = binomial()),
#     warning = function(w) w,
#     error = function(e) e
#   )
#   
#   # Check for convergence warnings or infinite coefficients
#   if (inherits(fit, "warning") || inherits(fit, "error") ||
#       any(is.infinite(coef(fit))) || !fit$converged) {
#     cat("⚠️ Problem with variable:", var, "\n")
#     problematic_vars <- c(problematic_vars, var)
#   }
# }
# 
# # Output
# cat("\nVariables causing potential separation:\n")
# print(problematic_vars)


```

```{r, echo=FALSE, message=FALSE, warning=FALSE}


# sh_vars_final <- setdiff(sh_vars, c("sh_egg_count", "sm_egg_count", "p1_avg"))
# 
# sh_y <- "sh_inf"
# # Build formula string
# sh_formula <- paste(sh_y, "~", paste(sh_vars_final, collapse = " + "))
# 
# # Fit logistic regression model
# sh_model <- glm(as.formula(sh_formula), data = train_df, family = "binomial")
# sh_cse <- vcovCL(sh_model, cluster = train_df$hhid_village)
# 
# # Apply coeftest with clustered SE
# sh_model_cse <- coeftest(sh_model, vcov. = sh_cse)
# sh_model_cse

```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

# problematic_vars <- c()
# 
# for (var in sh_vars_final) {
#   # Build the formula for a single predictor
#   f <- as.formula(paste("sh_inf ~", var))
#   
#   # Try to fit the model
#   fit <- tryCatch(
#     glm(f, data = train_df, family = binomial()),
#     warning = function(w) w,
#     error = function(e) e
#   )
#   
#   # Check for convergence warnings or infinite coefficients
#   if (inherits(fit, "warning") || inherits(fit, "error") ||
#       any(is.infinite(coef(fit))) || !fit$converged) {
#     cat("⚠️ Problem with variable:", var, "\n")
#     problematic_vars <- c(problematic_vars, var)
#   }
# }
# 
# # Output
# cat("\nVariables causing potential separation:\n")
# print(problematic_vars)
# 
# 
# problematic_vars <- c()
# 
# for (var in sh_vars_final) {
#   # Formula with one predictor against all others
#   other_vars <- setdiff(sh_vars_final, var)
#   f <- as.formula(paste(var, "~", paste(other_vars, collapse = "+")))
#   
#   # Fit linear model
#   fit <- tryCatch(
#     lm(f, data = train_df),
#     error = function(e) e
#   )
#   
#   # Check if model fit failed or R^2 very high (collinearity)
#   if (inherits(fit, "error")) {
#     cat("⚠️ Error fitting", var, "\n")
#     problematic_vars <- c(problematic_vars, var)
#   } else {
#     r2 <- summary(fit)$r.squared
#     if (!is.na(r2) && r2 > 0.9) {  # threshold can be changed
#       cat("⚠️ High collinearity detected for:", var, "(R^2 =", round(r2,3), ")\n")
#       problematic_vars <- c(problematic_vars, var)
#     }
#   }
# }
# 
# cat("\nVariables likely collinear:\n")
# print(problematic_vars)
# 
# 

```



#### Prediction - all


```{r, echo=FALSE, message=FALSE, warning=FALSE}

# test_probs <- predict(sh_model, newdata = test_df, type = "response")
# 
# head(test_probs)
# 
# # For example, classify as positive if prob > 0.5
# threshold <- 0.5
# test_pred_class <- ifelse(test_probs > threshold, 1, 0)
# 
# actual <- test_df$sh_inf
# 
# table(Predicted = test_pred_class, Actual = actual)


```

We will:

- **Compute predicted probabilities** for each individual using the model.
- **Threshold Selection**: Start with a 0.5 threshold for classifying individuals as infected (probability > 0.5) or uninfected (probability ≤ 0.5).
- **Confusion Matrix**: Generate a 2x2 confusion matrix comparing predicted versus actual infections (infected vs. non-infected).
  - **False Negative Rate (FNR)**: The proportion of actual infected individuals incorrectly predicted as uninfected.
  - **False Positive Rate (FPR)**: The proportion of uninfected individuals incorrectly predicted as infected.
- **Threshold Iteration**: Incrementally adjust the threshold (e.g., from 0.1 to 0.9) and recalculate the confusion matrix, FNR, and FPR at each step.
- **Optimization**: Identify the threshold that minimizes the combined classification error (FNR + FPR).


```{r, echo=FALSE, message=FALSE, warning=FALSE}

test_probs <- predict(sh_model, newdata = test_df, type = "response")


evaluate_thresholds <- function(test_probs, actual, thresholds = seq(0.1, 0.9, by = 0.1)) {
  results <- data.frame()
  
  for (threshold in thresholds) {
    pred_class <- ifelse(test_probs > threshold, 1, 0)
    
    TP <- sum(pred_class == 1 & actual == 1)
    TN <- sum(pred_class == 0 & actual == 0)
    FP <- sum(pred_class == 1 & actual == 0)
    FN <- sum(pred_class == 0 & actual == 1)
    
    FPR <- ifelse((FP + TN) > 0, FP / (FP + TN), NA)
    FNR <- ifelse((FN + TP) > 0, FN / (FN + TP), NA)
    Sum_FPR_FNR <- FPR + FNR
    
    results <- rbind(results, data.frame(
      Threshold = threshold,
      TP = TP, TN = TN, FP = FP, FN = FN,
      FPR = round(FPR, 3),
      FNR = round(FNR, 3),
      Sum_FPR_FNR = round(Sum_FPR_FNR, 3)
    ))
  }
  
  # Find threshold that minimizes FPR + FNR
  min_row <- results[which.min(results$Sum_FPR_FNR), ]
  attr(results, "best_threshold") <- min_row$Threshold
  
  return(results)
}
  

results_df <- evaluate_thresholds(test_probs, test_df$sh_inf)

kable(results_df, format = "html", caption = "Confusion Matrix for sh_inf at each threshold") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE, position = "left") %>%
  scroll_box(width = "100%")


# Best threshold (minimizing FPR + FNR)
sh_best_threshold <- attr(results_df, "best_threshold")


kable(sh_best_threshold, format = "html", caption = "Best threshold") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE, position = "left") %>%
  scroll_box(width = "100%")
##no variation - at any threshold, parasitological variables are able to nearly perfectly predict. 

```


#### Prediction - survey

Regression output from running logit regression using ONLY survey variables. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
sh_y <- "sh_inf"

sh_vars_survey <- c(
  "hh_age_", "hh_gender_", "hh_10_w99", "hh_12_6_", 
  "hh_37_", "health_5_3_1_", "health_5_3_3_", "health_5_3_6_", 
  "health_5_3_9_", "health_5_5_", "health_5_8_", "health_5_9_", 
  "living_01_bin", "living_04_bin", "beliefs_01_bin", "asset_index", 
  "q_51_w99"
)

# Build formula string
sh_formula_survey <- paste(sh_y, "~", paste(sh_vars_survey, collapse = " + "))

# Fit logistic regression model
sh_model2 <- glm(as.formula(sh_formula_survey), data = train_df, family = "binomial")
# sh_cse <- vcovCL(sh_model2, cluster = train_df$hhid_village)
# 
# # Apply coeftest with clustered SE
# sh_model_cse <- coeftest(sh_model2, vcov. = sh_cse)

print(sh_model2)

# See summary
#summary(sh_model_cse)


```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

# test_probs <- predict(sh_model, newdata = test_df, type = "response")
# 
# head(test_probs)
# 
# # For example, classify as positive if prob > 0.5
# threshold <- 0.5
# test_pred_class <- ifelse(test_probs > threshold, 1, 0)
# 
# actual <- test_df$sh_inf
# 
# table(Predicted = test_pred_class, Actual = actual)


```


```{r, echo=FALSE, message=FALSE, warning=FALSE}

test_probs <- predict(sh_model2, newdata = test_df, type = "response")



### Generalized to function 

evaluate_thresholds <- function(test_probs, actual, thresholds = seq(0.1, 0.9, by = 0.1)) {
  results <- data.frame()
  
  for (threshold in thresholds) {
    pred_class <- ifelse(test_probs > threshold, 1, 0)
    
    TP <- sum(pred_class == 1 & actual == 1)
    TN <- sum(pred_class == 0 & actual == 0)
    FP <- sum(pred_class == 1 & actual == 0)
    FN <- sum(pred_class == 0 & actual == 1)
    
    FPR <- ifelse((FP + TN) > 0, FP / (FP + TN), NA)
    FNR <- ifelse((FN + TP) > 0, FN / (FN + TP), NA)
    Sum_FPR_FNR <- FPR + FNR
    
    results <- rbind(results, data.frame(
      Threshold = threshold,
      TP = TP, TN = TN, FP = FP, FN = FN,
      FPR = round(FPR, 3),
      FNR = round(FNR, 3),
      Sum_FPR_FNR = round(Sum_FPR_FNR, 3)
    ))
  }
  
  # Find threshold that minimizes FPR + FNR
  min_row <- results[which.min(results$Sum_FPR_FNR), ]
  attr(results, "best_threshold") <- min_row$Threshold
  
  return(results)
}
  

results_df <- evaluate_thresholds(test_probs, test_df$sh_inf)
print(results_df)

# Best threshold (minimizing FPR + FNR)
sh_best_threshold_survey <- attr(results_df, "best_threshold")

kable(results_df, format = "html", caption = "Confusion Matrix for sh_inf at each threshold using only survey covariates") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE, position = "left") %>%
  scroll_box(width = "100%")



kable(sh_best_threshold_survey, format = "html", caption = "Survey Covariates Confusion Matrix Best Threshold") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = FALSE, position = "left") %>%
  scroll_box(width = "100%")

```


##### Summarize and visualize the probababilities

```{r, echo=FALSE, message=FALSE, warning=FALSE}
### visulalize 

summary(test_probs)
hist(test_probs, breaks = 20, col = "skyblue", main = "Distribution of Predicted Probabilities")




```














