---
title: "Balance_Tables"
author: "Kateri Mouawad"
date: "2025-01-03"
output: html_document
---

#Read Me

This script processes: 
  * baseline_balance_tables_data_PAP.dta

This script outputs:
  
  
  

#INITIATE SCRIPT
##START HERE - load packages

```{r}

library(dplyr)
library(readr)
library(tidyr)
library(haven)
library(data.table)
library(tidyverse)
library(estimatr)
library(broom)
library(kableExtra)
library(sandwich)
library(lmtest)

```


### Define file paths and load data 

```{r}

# Define the file paths
proj_paths <- list(
  projects = "C:/Users/Kateri/Box/NSF Senegal",
  alternative_projects = "C:/Users/km978/Box/NSF Senegal"
)

# Check if the Kateri path exists and resolve the project path accordingly
if (file.exists(proj_paths$projects)) {
  proj <- kwb.utils::resolve(list(
    projects = proj_paths$projects,
    p1 = "<projects>/Data_Management/Output/Data_Analysis/Balance_Tables"
  ))  
} else {
  proj <- kwb.utils::resolve(list(
    projects = proj_paths$alternative_projects,
    p1 = "<projects>/Data_Management/Output/Data_Analysis/Balance_Tables"
  ))
}


file_path_balance_tables_df <- file.path(proj$p1, "baseline_balance_tables_data_PAP.dta")
balance_df <- read_dta(file_path_balance_tables_df)
balance_df

```


####Filter data and transform to long


```{r}


# Adding a single categorical variable for household training categories
balance_df <- balance_df %>%
  mutate(
    # Extract the two middle characters (e.g., 2A) from hhid
    group = str_sub(hhid, 3, 4),
    
    # Assign treatment group based on the extracted group value
    treatment_group = case_when(
      group %in% c("0A", "0B") ~ "Control",
      group %in% c("1A", "1B") ~ "Treatment1", # Public health trained
      group %in% c("1A", "1B", "2A", "2B", "3A", "3B") & trained_hh == 0 ~ "Local Control",  # All Local Control
      group %in% c("2A", "2B") ~ "Treatment2", # Private benefits trained
      group %in% c("3A", "3B") ~ "Treatment3"  # Public and private trained
    )
  ) %>% select(-group, -trained_hh)

long_data <- balance_df %>%
  pivot_longer(
    cols = -c(hhid, hhid_village, treatment_group),  # Keep hhid and group as is, pivot all other columns
    names_to = "variable",    # Create a column named "variable" for former column names
    values_to = "value"       # Store values in a column named "value"
  )

  long_data <- long_data %>%
    rename(group = treatment_group)
  long_data



```


##Compute summary stats



```{r}



compute_summary_stats <- function(df) {
  df %>%
    group_by(group, variable) %>%
    summarise(
      mean_value = round(mean(value, na.rm = TRUE), 2),
      sd_value = round(sd(value, na.rm = TRUE), 2),
      .groups = "drop"  # Prevents group structure from persisting
    ) %>%
    pivot_longer(cols = c(mean_value, sd_value), names_to = "stat_type", values_to = "stat_value") %>%
    mutate(stat_type = ifelse(stat_type == "mean_value", "Mean", "SD")) %>%
    pivot_wider(names_from = group, values_from = stat_value) %>%
    arrange(variable, stat_type) %>%
    # This ensures the 'variable' and 'stat_type' columns come first
    select(variable, stat_type, everything()) %>%
    # Explicitly ensure 'variable' is ordered as it appears in the original data
    arrange(match(variable, unique(df$variable))) 
}

summary_table <- compute_summary_stats(long_data)

# View output
print(summary_table)



```


####Add survey questions and values 

```{r}

# index2 <- which(summary_table$variable == "hh_12_1_")
#   summary_table <- add_row(summary_table, variable = "hh_12", .before = index2)

# Add "hh_13_1_" above "hh_12"
# index3 <- which(summary_table$variable == "hh_13_01")
#   summary_table <- add_row(summary_table, variable = "hh_13", .before = index3)

# index5 <- which(summary_table$variable == "species_1")
#   final_summary_tabletable <- add_row(summary_table, variable = "species", .before = index5)

summary_table <- summary_table %>%
  mutate(
    variable = ifelse(stat_type == "SD" & !is.na(stat_type), "", variable),  # Clear variable for SD rows
    stat_type = ifelse(stat_type == "SD" & !is.na(stat_type), "", stat_type)  # Clear stat_type for SD rows
  ) %>%
  mutate(across(where(is.numeric), ~ format(.x, nsmall = 2))) %>%
  mutate(across(everything(), as.character)) %>%  # Ensure all columns are character type
  mutate(across(
    Control:Treatment3,  # Apply only to numeric columns
    ~ ifelse(stat_type == "", paste0("(", trimws(.), ")"), .)  # Add parentheses for SD values
  ))


summary_table

summary_table <- summary_table %>%
  mutate(Question = case_when(
    variable == "hhid_village" ~ "Village ID",
    variable == "hhid" ~ "Household ID",
    variable == "trained_hh" ~ "Trained household",
    variable == "hh_age_h" ~ "Household head age",
    variable == "hh_education_level_bin_h" ~ "Indicator for household head with secondary education or higher (1=Yes, 0=No)",
    variable == "hh_education_skills_5_h" ~ "Indicator that household head is literate (1=Yes, 0=No)",
    variable == "hh_gender_h" ~ "Household head gender (1=Male, 0=Female)",
    variable == "hh_numero" ~ "Size of household",
    
    variable == "hh_03_" ~ "Indicator for those who worked in domestic agricultural activities (1=Yes, 0=No) †",
    variable == "hh_10_" ~ "Hours per week spent within 1 meter of surface water source",
    variable == "hh_12_6_" ~ "Indicator for those who harvested aquatic vegetation, among those who spent time near a water source (1=Yes, 0=No)",
    variable == "hh_16_" ~ "Hours spent producing, purchasing, or applying fertilizer",
    variable == "hh_15_2" ~ "Indicator for making fertilizer (compost) among those who spent time near a water source (1=Yes, 0=No)",
    
    variable == "hh_26_" ~ "Indicator if currently enrolled in formal school (1=Yes, 0=No, asked to children) †",
    variable == "hh_27_" ~ "Indicator if attended non-formal school or training? (1=Yes, 0=No, asked to children) †",
    variable == "hh_29_bin" ~ "Indicator if achieved any level higher than primary grade (1=Yes, 0=No, asked to children)",
    variable == "hh_31_bin" ~ "Indicator if student completed studies or moved to next class (1=Yes, 0=No, asked to children)",
    variable == "hh_37_" ~ "Indicator if missed >1 consecutive week of school due to illness? (1=Yes, 0=No, asked to children) †",
    variable == "hh_38_" ~ "Number of attended school days in the past week (Asked to children)",
    
    variable == "living_01_bin" ~ "Indicator for selected tap water as main drinking source (1=Yes, 0=No)",
    variable == "game_A_total" ~ "Total paid for Game A (CFA)",
    variable == "game_B_total" ~ "Total paid for Game B (CFA)",
    
    variable == "TLU" ~ "Tropical livestock units",
    variable == "agri_6_15" ~ "Number of cultivated plots",
    variable == "agri_6_32_bin" ~ "Indicator if used any organic fertilizer (1=Yes, 0=No)",
    variable == "agri_6_36_bin" ~ "Indicator if used any inorganic/chemical fertilizer (1=Yes, 0=No)",
    variable == "total_land_ha" ~ "Total land owned (hectares)",
    variable == "agri_6_34_comp_any" ~ "Used any compost on any parcel (1=Yes, 0=No) †",
    
    variable == "agri_income_01" ~ "Indicator if engaged in paid agricultural work in last 12 months (1=Yes, 0=No) †",
    variable == "agri_income_05" ~ "Amount received for agricultural work",
    
    variable == "beliefs_01_bin" ~ "Probability of contracting bilharzia (1=Strongly agree/Agree) +",
    variable == "beliefs_02_bin" ~ "Probability of household member contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_03_bin" ~ "Probability of a child contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_04_bin" ~ "Agree: Village land should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_05_bin" ~ "Agree: Village water sources should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_06_bin" ~ "Agree: Right to products from own land (1=Yes, 0=No) +",
    variable == "beliefs_07_bin" ~ "Agree: Right to products from community land worked on (1=Yes, 0=No) +",
    variable == "beliefs_08_bin" ~ "Agree: Right to products from community water sources fished in (1=Yes, 0=No) +",
    variable == "beliefs_09_bin" ~ "Agree: Right to products from community water sources harvested from (1=Yes, 0=No) +",
    
    variable == "health_5_3_bin" ~ "Indicator for bilharzia or diarrhea in the past 12 months (1=Yes, 0=No, among those reporting illness)",
    variable == "health_5_6_" ~ "Indicator for Diagnosed with schistosomiasis (1=Yes, 0=No) †",
    
    variable == "num_water_access_points" ~ "Number of village water access points",
    variable == "q_51" ~ "Distance to nearest healthcare center (km) [village level]",
    variable == "target_village" ~ "Indicator if auction village (1=Yes, 0=No)",
    
    TRUE ~ variable  # Default case
  ))


summary_table <- summary_table %>% select(Question, everything()) %>%
  select(-"stat_type")  %>%
  rename(Variable = variable,
         `Private Treatment` = Treatment1,
         `Public Treatment` = Treatment2, 
         `Private and Public Treatment` = Treatment3)
summary_table
#%>%   filter(variable != "target_village")

# Set working directory
setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")

# Create table with footnotes using kableExtra
summary_table %>%
  kable(format = "html", escape = FALSE, caption = "Summary Table") %>%
  footnote(
    general = "Standard deviations in parentheses.",
    symbol = c(
      "† Indicates that the 2's from the 'I Don't know' option have been replaced with missing.",
      "+ Indicates that these binaries were created from Likert scale variables based on response distribution."
    )
  ) %>%
  save_kable("SS_balance_tableV2.html")

```
###Output table

```{r}
setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")

# Create table with footnotes using kableExtra
summary_table %>%
  kable(format = "html", escape = FALSE, caption = "Summary Table") %>%
  footnote(
    general = "Standard deviations in parentheses.",
    symbol = c(
      "† Indicates that the 2's from the 'I Don't know' option have been replaced with missing.",
      "+ Indicates that these binaries were created from Likert scale variables based on response distribution."
    )
  ) %>%
  save_kable("SS_balance_tableV2.html")
```


##Compute t-stats and cluster SEs at the village level



```{r}

#<><<><><>><><<><><>>
#CREATE REGRESSION FUNCTION
#<><<><><>><><<><><>>
      # This is a double nested loop 
      # The first part runs the function on the arms
      # The second part runs the function on the variables

run_regressions <- function(data, treatment_col, village_col, vars_to_test) {
  results <- list()
  for (var in vars_to_test) {
    treatments <- unique(data[[treatment_col]])
    treatments <- setdiff(treatments, 'Control')
    for (arm in treatments) {
      subset <- data %>% filter(.data[[treatment_col]] %in% c('Control', arm) & variable == var)
      subset$treat <- ifelse(subset[[treatment_col]] == arm, 1, 0)
      model <- lm(value ~ treat, data = subset)
      clustered_se <- coeftest(model, vcov = vcovCL(model, cluster = subset[[village_col]]))
      results <- append(results, list(data.frame(variable = var, comparison = paste('Control vs', arm), 
                                                 stat = round(clustered_se[2, 3], 2), 
                                                 p = round(clustered_se[2, 4], 2))))
    }
    for (i in 1:(length(treatments) - 1)) {
      for (j in (i + 1):length(treatments)) {
        subset <- data %>% filter(.data[[treatment_col]] %in% c(treatments[i], treatments[j]) & variable == var)
        subset$treat <- ifelse(subset[[treatment_col]] == treatments[j], 1, 0)
        model <- lm(value ~ treat, data = subset)
        clustered_se <- coeftest(model, vcov = vcovCL(model, cluster = subset[[village_col]]))
        results <- append(results, list(data.frame(variable = var, comparison = paste(treatments[i], 'vs', treatments[j]), 
                                                 stat = round(clustered_se[2, 3], 2), 
                                                 p = round(clustered_se[2, 4], 2))))
      }
    }
  }
  bind_rows(results)
}

    vars_to_test_reg <- setdiff(names(balance_df), c("hhid", "hhid_village", "treatment_group"))
    regression_results <- run_regressions(long_data, 'group', 'hhid_village', vars_to_test_reg)
regression_results
#<><<><><>><><<><><>>
#CREATE F-STAT FUNCTION FOR EACH VAR
#<><<><><>><><<><><>>

# Function to perform F-test for each variable
run_f_tests <- function(data, treatment_col, vars_to_test) {
  results <- list()
  
  for (var in vars_to_test) {
    # Construct formula dynamically (e.g., hh_15_2 ~ group)
    formula <- as.formula(paste(var, "~", treatment_col))
        # Run ANOVA for each variable
    anova_result <- aov(formula, data = data)
        # Get the F-statistic and p-value
    f_stat <- summary(anova_result)[[1]]$`F value`[1]
    p_value <- summary(anova_result)[[1]]$`Pr(>F)`[1]
    
    # Store results
    results <- append(results, list(data.frame(variable = var, 
                                               f_statistic = round(f_stat, 2), 
                                               p_value = round(p_value, 4))))
  }
  # Combine and return the results as a data frame
  return(bind_rows(results))
}
    vars_to_test_fstat <- setdiff(names(balance_df), c("hhid", "hhid_village", "treatment_group"))
    # Example usage
    f_test_results <- run_f_tests(balance_df, treatment_col = "treatment_group", vars_to_test = vars_to_test_fstat)
    print(f_test_results)



#<><<><><>><><<><><>>
#CREATE F-STAT FUNCTION FOR TREATMENT ARM
#<><<><><>><><<><><>>

# Function to compute Joint F-statistics for each treatment arm (Wide Format)
run_pairwise_f_test <- function(data, treatment_col, vars_to_test) {
  results <- list()
  
  # Get all treatment arms (excluding 'Control')
  treatments <- unique(data[[treatment_col]])
  treatments <- treatments[treatments != "Control"]
  
  # Loop over all pairwise combinations of treatments
  for (i in 1:(length(treatments) - 1)) {
    for (j in (i + 1):length(treatments)) {
      # Subset the data for the current pair of treatments
      subset <- data[data[[treatment_col]] %in% c(treatments[i], treatments[j]), ]
      
      # Create regression formula (e.g., hh_15_2 + hh_26_ + hh_27_ ~ group)
      formula <- as.formula(paste(paste(vars_to_test, collapse = " + "), "~", treatment_col))
      
      # Run the regression model
      model <- lm(formula, data = subset)
      
      # Compute F-statistic for the joint test
      f_stat <- summary(model)$fstatistic[1]
      p_value <- pf(f_stat, df1 = summary(model)$fstatistic[2], df2 = summary(model)$fstatistic[3], lower.tail = FALSE)
      
      # Store results for this pairwise comparison
      results <- append(results, list(data.frame(treatment_comparison = paste(treatments[i], "vs", treatments[j]),
                                                 f_statistic = round(f_stat, 2), 
                                                 p_value = round(p_value, 4))))
    }
  }
  
  # Combine and return the results as a data frame
  return(bind_rows(results))
}

 vars_to_test_fjoint <- setdiff(names(balance_df), c("hhid", "hhid_village", "treatment_group"))
    joint_f_test_results <- run_pairwise_f_test(balance_df, treatment_col = "treatment_group", vars_to_test = vars_to_test_fjoint)


   

# Print results
print(joint_f_test_results)
print(f_test_results)
regression_results



```



##Create completed table


```{r}


# Pivot the table to have variables as rows and comparisons as columns
final_table <- regression_results %>%
  pivot_wider(names_from = comparison, values_from = c(stat, p))

# Rearrange to stack t-stats and p-values in rows
final_table <- final_table %>%
  pivot_longer(cols = -variable, names_to = 'comparison', values_to = 'value') %>%
  separate(comparison, into = c('type', 'comparison'), sep = '_', extra = 'merge') %>%
  pivot_wider(names_from = comparison, values_from = value)

# Merge F-statistics data into final_table
final_table <- final_table %>%
  left_join(f_test_results, by = "variable")

# Replace the value underneath f_stat with p_value
final_table <- final_table %>%
  mutate(across(starts_with("f_stat"), ~ ifelse(type == "p", as.character(p_value), as.character(.)))) %>%
  mutate(across(where(is.numeric), ~ format(.x, nsmall = 2))) %>%  # Ensure 2 decimal places
  mutate(across(everything(), as.character)) %>%  # Convert all to character
  mutate(across(everything(), ~ ifelse(grepl("p", type), paste0("(", trimws(.x), ")"), .x)))  # Format p-values with parentheses

# Print the final formatted table
print(final_table)

##Issue here - figure out how to append bottom row

f_stats_row <- data.frame(
  variable = "F statistics of Joint F-test:", 
  treatment1_vs_treatment2 = joint_f_test_results$f_statistic_Treatment1_vs_Treatment2[1], 
  treatment1_vs_local_control = joint_f_test_results$f_statistic_Treatment1_vs_Local_Control[1], 
  treatment1_vs_treatment3 = joint_f_test_results$f_statistic_Treatment1_vs_Treatment3[1],
  treatment2_vs_local_control = joint_f_test_results$f_statistic_Treatment2_vs_Local_Control[1],
  treatment2_vs_treatment3 = joint_f_test_results$f_statistic_Treatment2_vs_Treatment3[1]
)

p_values_row <- data.frame(
  variable = "P-value", 
  treatment1_vs_treatment2 = paste0("(", round(joint_f_test_results$p_value_Treatment1_vs_Treatment2[1], 4), ")"), 
  treatment1_vs_local_control = paste0("(", round(joint_f_test_results$p_value_Treatment1_vs_Local_Control[1], 4), ")"), 
  treatment1_vs_treatment3 = paste0("(", round(joint_f_test_results$p_value_Treatment1_vs_Treatment3[1], 4), ")"),
  treatment2_vs_local_control = paste0("(", round(joint_f_test_results$p_value_Treatment2_vs_Local_Control[1], 4), ")"),
  treatment2_vs_treatment3 = paste0("(", round(joint_f_test_results$p_value_Treatment2_vs_Treatment3[1], 4), ")")
)

# Combine pairwise results and append the F-stat and P-value rows
final_table <- bind_rows(pairwise_f_test_results, f_stats_row, p_values_row)

# Print the final table
print(final_table)









    # Convert t-stat and p-value to numeric and round to two decimal places
#     merged_results <- merged_results %>%
#       mutate(across(c(stat, p), ~ round(.x, 2))) 
# 
#     # Pivot the table to have variables as rows and comparisons as columns
#     final_table <- merged_results %>%
#       pivot_wider(names_from = comparison, values_from = c(stat, p))
# final_table
#     # Rearrange to stack t-stats and p-values in rows
#     final_table <- final_table %>%
#       pivot_longer(cols = -variable, names_to = 'comparison', values_to = 'value') %>%
#       separate(comparison, into = c('type', 'comparison'), sep = '_', extra = 'merge') %>%
#       pivot_wider(names_from = comparison, values_from = value)
# 
#     # Add formatting to ensure two decimal places for all numeric values (t-stats and p-values)
#     final_table <- final_table %>%
#       mutate(across(where(is.numeric), ~ format(.x, nsmall = 2))) %>%  # Format with 2 decimals
#       mutate(across(everything(), as.character)) %>%  # Ensure all columns are characters
#       mutate(across(everything(), ~ ifelse(grepl("p", type),
#                                            paste0("(", trimws(.x), ")"),  # Trim any extra spaces around the value
#                                            .x)))  # Add parentheses for p.value rows
#     # Clean up column names (variable and type) for p-values
# 
# print(final_table)
# 
# 
# 
# 
#     # Convert t-stat and p-value to numeric and round to two decimal places
#     regression_results <- regression_results %>%
#       mutate(across(c(stat, p), ~ round(.x, 2)))
# 
#     # Pivot the table to have variables as rows and comparisons as columns
#     final_table <- regression_results %>%
#       pivot_wider(names_from = comparison, values_from = c(stat, p))
# final_table
#     # Rearrange to stack t-stats and p-values in rows
#     final_table <- final_table %>%
#       pivot_longer(cols = -variable, names_to = 'comparison', values_to = 'value') %>%
#       separate(comparison, into = c('type', 'comparison'), sep = '_', extra = 'merge') %>%
#       pivot_wider(names_from = comparison, values_from = value)
# 
#     # Add formatting to ensure two decimal places for all numeric values (t-stats and p-values)
#     final_table <- final_table %>%
#       mutate(across(where(is.numeric), ~ format(.x, nsmall = 2))) %>%  # Format with 2 decimals
#       mutate(across(everything(), as.character)) %>%  # Ensure all columns are characters
#       mutate(across(everything(), ~ ifelse(grepl("p", type),
#                                            paste0("(", trimws(.x), ")"),  # Trim any extra spaces around the value
#                                            .x)))  # Add parentheses for p.value rows
#     # Clean up column names (variable and type) for p-values
# 
# print(final_table)






















```





















####Add survey questions and values 

```{r}

final_table <- final_table %>%
  mutate(
    variable = if_else(type == "(p)", "", variable),  # Clear variable when type == "(p)"
    type = if_else(type == "(p)", "", type) # Clear type when type == "(p)"
  ) %>%
  select(-type)  # Remove the 'type' column after modification


final_table <- final_table %>%
  mutate(Question = case_when(
    variable == "hhid_village" ~ "Village ID",
    variable == "hhid" ~ "Household ID",
    variable == "trained_hh" ~ "Trained household",
    variable == "hh_age_h" ~ "Household head age",
    variable == "hh_education_level_bin_h" ~ "Indicator for household head with secondary education or higher (1=Yes, 0=No)",
    variable == "hh_education_skills_5_h" ~ "Indicator that household head is literate (1=Yes, 0=No)",
    variable == "hh_gender_h" ~ "Household head gender (1=Male, 0=Female)",
    variable == "hh_numero" ~ "Size of household",
    
    variable == "hh_03_" ~ "Indicator for those who worked in domestic agricultural activities (1=Yes, 0=No) †",
    variable == "hh_10_" ~ "Hours per week spent within 1 meter of surface water source",
    variable == "hh_12_6_" ~ "Indicator for those who harvested aquatic vegetation, among those who spent time near a water source (1=Yes, 0=No)",
    variable == "hh_16_" ~ "Hours spent producing, purchasing, or applying fertilizer",
    variable == "hh_15_2" ~ "Indicator for making fertilizer (compost) among those who spent time near a water source (1=Yes, 0=No)",
    
    variable == "hh_26_" ~ "Indicator if currently enrolled in formal school (1=Yes, 0=No, asked to children) †",
    variable == "hh_27_" ~ "Indicator if attended non-formal school or training? (1=Yes, 0=No, asked to children) †",
    variable == "hh_29_bin" ~ "Indicator if achieved any level higher than primary grade (1=Yes, 0=No, asked to children)",
    variable == "hh_31_bin" ~ "Indicator if student completed studies or moved to next class (1=Yes, 0=No, asked to children)",
    variable == "hh_37_" ~ "Indicator if missed >1 consecutive week of school due to illness? (1=Yes, 0=No, asked to children) †",
    variable == "hh_38_" ~ "Number of attended school days in the past week (Asked to children)",
    
    variable == "living_01_bin" ~ "Indicator for selected tap water as main drinking source (1=Yes, 0=No)",
    variable == "game_A_total" ~ "Total paid for Game A (CFA)",
    variable == "game_B_total" ~ "Total paid for Game B (CFA)",
    
    variable == "TLU" ~ "Tropical livestock units",
    variable == "agri_6_15" ~ "Number of cultivated plots",
    variable == "agri_6_32_bin" ~ "Indicator if used any organic fertilizer (1=Yes, 0=No)",
    variable == "agri_6_36_bin" ~ "Indicator if used any inorganic/chemical fertilizer (1=Yes, 0=No)",
    variable == "total_land_ha" ~ "Total land owned (hectares)",
    variable == "agri_6_34_comp_any" ~ "Used any compost on any parcel (1=Yes, 0=No) †",
    
    variable == "agri_income_01" ~ "Indicator if engaged in paid agricultural work in last 12 months (1=Yes, 0=No) †",
    variable == "agri_income_05" ~ "Amount received for agricultural work",
    
    variable == "beliefs_01_bin" ~ "Probability of contracting bilharzia (1=Strongly agree/Agree) +",
    variable == "beliefs_02_bin" ~ "Probability of household member contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_03_bin" ~ "Probability of a child contracting bilharzia (1=Yes, 0=No) +",
    variable == "beliefs_04_bin" ~ "Agree: Village land should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_05_bin" ~ "Agree: Village water sources should belong to community (1=Yes, 0=No) +",
    variable == "beliefs_06_bin" ~ "Agree: Right to products from own land (1=Yes, 0=No) +",
    variable == "beliefs_07_bin" ~ "Agree: Right to products from community land worked on (1=Yes, 0=No) +",
    variable == "beliefs_08_bin" ~ "Agree: Right to products from community water sources fished in (1=Yes, 0=No) +",
    variable == "beliefs_09_bin" ~ "Agree: Right to products from community water sources harvested from (1=Yes, 0=No) +",
    
    variable == "health_5_3_bin" ~ "Indicator for bilharzia or diarrhea in the past 12 months (1=Yes, 0=No, among those reporting illness)",
    variable == "health_5_6_" ~ "Indicator for Diagnosed with schistosomiasis (1=Yes, 0=No) †",
    
    variable == "num_water_access_points" ~ "Number of village water access points",
    variable == "q_51" ~ "Distance to nearest healthcare center (km) [village level]",
    variable == "target_village" ~ "Indicator if auction village (1=Yes, 0=No)",
    
    TRUE ~ variable  # Default case
  ))

final_table <- final_table %>% select(Question, everything()) %>%
  rename(Variable = variable,
         `Control vs Private Treatment` = `Control vs Treatment1`,
          `Control vs Public Treatment` = `Control vs Treatment2`,
          `Control vs Public & Private Treatment` = `Control vs Treatment3`,
          `Private Treatment vs Public Treatment` = `Treatment1 vs Treatment2`,
          `Private Treatment vs Public & Private Treatment` = `Treatment1 vs Treatment3`,
          `Public Treatment vs Public & Private Treatment` = `Treatment2 vs Treatment3`)

final_table
```

###Output table
```{r}


setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")

final_table %>%
  kable(format = "html", escape = FALSE, caption = "Balance Table") %>%
  footnote(
    general = "P-values in parentheses. Standard errors are clustered at the village level.",
    symbol = c(
      "† Indicates that the 2's from the 'I Don't know' option have been replaced with missing.",
      "+ Indicates that these binaries were created from Likert scale variables based on response distribution."
    )
  ) %>%
  save_kable("balance_tablev3.html")

# setwd("C:/Users/km978/Box/NSF Senegal/Data_Management/Output/Data_Analysis/Balance_Tables")
# knitr::kable(final_table, format = "html") %>% save_kable("balance_tablev3.html")

```


















